---
title: "Color y recompensas"
author: "Marcial"
date: "01/09/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---
1. Install and load packages

```{r, echo = F}
#library("devtools")
#devtools::install_github("jinyizju/V.PhyloMaker2")
library(V.PhyloMaker2)

# github (requires `remotes` or `devtools`)
#devtools::install_github("ecoinfor/U.Taxonstand")
library(U.Taxonstand)

```


3. Frequency matrix.

```{r, echo = F}
mydata <- read.csv("./PIGMENT_EVOLUTION_V7.csv") 
dim(mydata)
```



3. Create your tree and plot

```{r, echo = F}

# load the database

library(openxlsx)
#dat1 <- read.xlsx("WFO_v2.1_20230304_part1.xlsx")
#dat2 <- read.xlsx("WFO_v2.1_20230304_part2.xlsx")
#dat3 <- read.xlsx("WFO_v2.1_20230304_part3.xlsx")
dat1 <- read.xlsx("Plants_WP_database_part1.xlsx")
dat2 <- read.xlsx("Plants_WP_database_part2.xlsx")
dat3 <- read.xlsx("Plants_WP_database_part3.xlsx")
database <- rbind(dat1, dat2, dat3)
#We are going to use the WP database but there are many differnt options
#Check here https://github.com/nameMatch/Database/tree/main

rm(dat1, dat2, dat3)

corrected.species <- nameMatch(mydata$Species..names.WFO.2,spSource=database, author = FALSE, max.distance= 1, matchFirst=TRUE)

corrected.species
#make corrections to your database if necessary
names(corrected.species)
write.csv(corrected.species, file = "corrected.species.csv")

c1<- corrected.species$Accepted_SPNAME
c2<- corrected.species$Genus_in_database
c3<- corrected.species$Family
mydata2 <- data.frame(species = c1, genus = c2, family = c3)

mytree <- phylo.maker(sp.list = mydata2, tree = GBOTB.extended.WP, nodes = nodes.info.1.WP, scenarios = "S2")
#There is available S1 and S3 and nodes.info.2.WP.csv

plot(mytree$scenario.2, cex = 0.5)





pdffn = paste0("myphylo", ".scenario2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(mytree$scenario.2, cex = 0.5)
dev.off()
write.tree(my.phylo.maker$scenario.2, file = "mytree2.tree")



```



Analyses with corHMM
```{r}

library(corHMM)

names(mydata)
mydata <- cbind(mydata,corrected.species$Accepted_SPNAME)
names(mydata)[12]<-"Accepted_SPNAME"
mydata[,12]<- gsub(" ", "_", mydata[,12])


Anthocyanins <- cbind (as.character(mydata[,12][!is.na(mydata[,7])]),mydata[,7][!is.na(mydata[,7])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Anthocyanins[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Anthocyanins.ARD.2<-corHMM(tree,Anthocyanins,rate.cat=2,node.states="marginal")
pp.Anthocyanins.ARD.2
pp.Anthocyanins.ARD.1<-corHMM(tree,Anthocyanins,rate.cat=1,node.states="marginal")
pp.Anthocyanins.ARD.1
pp.Anthocyanins.ER.2<-corHMM(tree,Anthocyanins,rate.cat=2, model = "ER", node.states="marginal")
pp.Anthocyanins.ER.2
pp.Anthocyanins.ER.1<-corHMM(tree,Anthocyanins,rate.cat=1, model = "ER", node.states="marginal")
pp.Anthocyanins.ER.1
pp.Anthocyanins.ARD.3<-corHMM(tree,Anthocyanins,rate.cat=3, node.states="marginal")
pp.Anthocyanins.ARD.3
pp.Anthocyanins.ER.3<-corHMM(tree,Anthocyanins,rate.cat=3, model = "ER", node.states="marginal")
pp.Anthocyanins.ER.3

simmap.Anthocyanins <- makeSimmap(tree=tree, data=Anthocyanins, model=pp.Anthocyanins.ER.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Anthocyanins)

pdffn = paste0("Model.Anthocyanins2rates.ER.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Anthocyanins.ER.2)
dev.off()

pdffn = paste0("Anthocyanins2rates.ER.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Anthocyanins.ER.2$states,cex=0.5, pie.cex=0.5,title="Anthocyanins 2 rates ER")
dev.off()

cols<-setNames(c("white", "black", "red", "yellow"),levels(c("(0,R1)", "(1,R1)", "(0,R2)", "(1,R2)")))
pdffn = paste0("Anthocyanins2ratesfanER.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Anthocyanins.2$states,piecol=cols,cex=0.2)
dev.off()

#Aurones
Aurones <- cbind (as.character(mydata[,12][!is.na(mydata[,8])]),mydata[,8][!is.na(mydata[,8])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Aurones[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Aurones.ARD.2<-corHMM(tree,Aurones,rate.cat=2,node.states="marginal")
pp.Aurones.ARD.2
pp.Aurones.ARD.1<-corHMM(tree,Aurones,rate.cat=1,node.states="marginal")
pp.Aurones.ARD.1
pp.Aurones.ER.2<-corHMM(tree,Aurones,rate.cat=2, model = "ER", node.states="marginal")
pp.Aurones.ER.2
pp.Aurones.ER.1<-corHMM(tree,Aurones,rate.cat=1, model = "ER", node.states="marginal")
pp.Aurones.ER.1
pp.Aurones.ARD.3<-corHMM(tree,Aurones,rate.cat=3, node.states="marginal")
pp.Aurones.ARD.3
pp.Aurones.ER.3<-corHMM(tree,Aurones,rate.cat=3, model = "ER", node.states="marginal")
pp.Aurones.ER.3

simmap.Aurones <- makeSimmap(tree=tree, data=Aurones, model=pp.Aurones.ARD.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Aurones)

pdffn = paste0("Model.Aurones2rates.ARD.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Aurones.ARD.2)
dev.off()

pdffn = paste0("Aurones2rates.ARD.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Aurones.ARD.2$states,cex=0.5, pie.cex=0.5,title="Aurones 2 rates ARD")
dev.off()

cols<-setNames(c("white", "black", "red", "yellow"),levels(c("(0,R1)", "(1,R1)", "(0,R2)", "(1,R2)")))
pdffn = paste0("Aurones2ratesfanARD.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Aurones.ARD.2$states,piecol=cols,cex=0.2)
dev.off()

#Carotenoids
Carotenoids <- cbind (as.character(mydata[,12][!is.na(mydata[,9])]),mydata[,9][!is.na(mydata[,9])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Carotenoids[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Carotenoids.ARD.2<-corHMM(tree,Carotenoids,rate.cat=2,node.states="marginal")
pp.Carotenoids.ARD.2
pp.Carotenoids.ARD.1<-corHMM(tree,Carotenoids,rate.cat=1,node.states="marginal")
pp.Carotenoids.ARD.1
pp.Carotenoids.ER.2<-corHMM(tree,Carotenoids,rate.cat=2, model = "ER", node.states="marginal")
pp.Carotenoids.ER.2
pp.Carotenoids.ER.1<-corHMM(tree,Carotenoids,rate.cat=1, model = "ER", node.states="marginal")
pp.Carotenoids.ER.1
pp.Carotenoids.ARD.3<-corHMM(tree,Carotenoids,rate.cat=3, node.states="marginal")
pp.Carotenoids.ARD.3
pp.Carotenoids.ER.3<-corHMM(tree,Carotenoids,rate.cat=3, model = "ER", node.states="marginal")
pp.Carotenoids.ER.3

simmap.Carotenoids <- makeSimmap(tree=tree, data=Carotenoids, model=pp.Carotenoids.ARD.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Carotenoids)

pdffn = paste0("Model.Carotenoids2rates.ARD.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Carotenoids.ARD.2)
dev.off()

pdffn = paste0("Carotenoids2rates.ARD.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Carotenoids.ARD.2$states,cex=0.5, pie.cex=0.5,title="Carotenoids 2 rates ARD")
dev.off()

cols<-setNames(c("white", "black", "red", "yellow"),levels(c("(0,R1)", "(1,R1)", "(0,R2)", "(1,R2)")))
pdffn = paste0("Carotenoids2ratesfanARD.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Carotenoids.ARD.2$states,piecol=cols,cex=0.2)
dev.off()


#Chlorophylls
Chlorophylls <- cbind (as.character(mydata[,12][!is.na(mydata[,10])]),mydata[,10][!is.na(mydata[,10])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Chlorophylls[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Chlorophylls.ARD.2<-corHMM(tree,Chlorophylls,rate.cat=2,node.states="marginal")
pp.Chlorophylls.ARD.2
pp.Chlorophylls.ARD.1<-corHMM(tree,Chlorophylls,rate.cat=1,node.states="marginal")
pp.Chlorophylls.ARD.1
pp.Chlorophylls.ER.2<-corHMM(tree,Chlorophylls,rate.cat=2, model = "ER", node.states="marginal")
pp.Chlorophylls.ER.2
pp.Chlorophylls.ER.1<-corHMM(tree,Chlorophylls,rate.cat=1, model = "ER", node.states="marginal")
pp.Chlorophylls.ER.1
pp.Chlorophylls.ARD.3<-corHMM(tree,Chlorophylls,rate.cat=3, node.states="marginal")
pp.Chlorophylls.ARD.3
pp.Chlorophylls.ER.3<-corHMM(tree,Chlorophylls,rate.cat=3, model = "ER", node.states="marginal")
pp.Chlorophylls.ER.3

simmap.Chlorophylls <- makeSimmap(tree=tree, data=Chlorophylls, model=pp.Chlorophylls.ARD.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Chlorophylls)

pdffn = paste0("Model.Chlorophylls2rates.ARD.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Chlorophylls.ARD.2)
dev.off()

pdffn = paste0("Chlorophylls2rates.ARD.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Chlorophylls.ARD.2$states,cex=0.5, pie.cex=0.5,title="Chlorophylls 2 rates ARD")
dev.off()

cols<-setNames(c("white", "black", "red", "yellow"),levels(c("(0,R1)", "(1,R1)", "(0,R2)", "(1,R2)")))
pdffn = paste0("Chlorophylls2ratesfanARD.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Chlorophylls.ARD.2$states,piecol=cols,cex=0.2)
dev.off()


#Npigments
Npigments <- cbind (as.character(mydata[,12][!is.na(mydata[,11])]),mydata[,11][!is.na(mydata[,11])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Npigments[,1])
tree <- drop.tip(tree, tipstoremove)

Npigments_LegendAndRate <- getStateMat4Dat(Npigments)
STEP <- dropStateMatPars(Npigments_LegendAndRate$rate.mat, c(7,10,11,2,3,6))
STEP
RateClassMat <- getRateCatMat(2)
RateClassMat
StateMats <- list(STEP, STEP)
StateMats
STEP2 <- getFullMat(StateMats, RateClassMat)

pp.Npigments.ARD.2<-corHMM(tree,Npigments,rate.cat=2,node.states="marginal")
pp.Npigments.ARD.2
pp.Npigments.ARD.1<-corHMM(tree,Npigments,rate.cat=1,node.states="marginal")
pp.Npigments.ARD.1
pp.Npigments.ER.2<-corHMM(tree,Npigments,rate.cat=2, model = "ER", node.states="marginal")
pp.Npigments.ER.2
pp.Npigments.ER.1<-corHMM(tree,Npigments,rate.cat=1, model = "ER", node.states="marginal")
pp.Npigments.ER.1
pp.Npigments.SYM.2<-corHMM(tree,Npigments,rate.cat=2, model = "SYM", node.states="marginal")
pp.Npigments.SYM.2
pp.Npigments.SYM.1<-corHMM(tree,Npigments,rate.cat=1, model = "SYM", node.states="marginal")
pp.Npigments.SYM.1
pp.Npigments.STEP.2<-corHMM(tree,Npigments,rate.cat=2, rate.mat=STEP2, node.states="marginal")
pp.Npigments.STEP.2
pp.Npigments.STEP.1<-corHMM(tree,Npigments,rate.cat=1, rate.mat=STEP, node.states="marginal")
pp.Npigments.STEP.1

#pp.Npigments.ARD.3<-corHMM(tree,Npigments,rate.cat=3, node.states="marginal")
#pp.Npigments.ARD.3
#pp.Npigments.ER.3<-corHMM(tree,Npigments,rate.cat=3, model = "ER", node.states="marginal")
#pp.Npigments.ER.3

simmap.Npigments <- makeSimmap(tree=tree, data=Npigments, model=pp.Npigments.STEP.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Npigments)

pdffn = paste0("Model.Npigments2rates.STEP.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Npigments.STEP.2)
dev.off()

pdffn = paste0("Npigments2rates.STEP.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Npigments.STEP.2$states,cex=0.5, pie.cex=0.5,title="Npigments 2 rates STEP")
dev.off()

cols<-setNames(c("white", "grey", "darkgrey", "black", "yellow", "orange", "red", "darkred"),levels(c("(0,R1)", "(1,R1)", "(2,R1)", "(3,R1)", "(0,R2)", "(1,R2)", "(2,R2)", "(3,R2)")))
pdffn = paste0("Npigments2ratesfanARD.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Npigments.ARD.2$states,piecol=cols,cex=0.2)
dev.off()

```

Independent vs. dependent evolution with corHMM

```{r}

library(corHMM)


#Anthocyanins.Aurones
Anthocyanins.Aurones <- cbind (as.character(mydata[,12][!is.na(mydata[,7]) & !is.na(mydata[,8])]),mydata[,7][!is.na(mydata[,7])& !is.na(mydata[,8])],mydata[,8][!is.na(mydata[,7])& !is.na(mydata[,8])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Anthocyanins.Aurones[,1])
tree <- drop.tip(tree, tipstoremove)

Anthocyanins.Aurones_LegendAndRate <- getStateMat4Dat(Anthocyanins.Aurones) 
Anthocyanins.Aurones_LegendAndRate
Anthocyanins.Aurones.ind <- Anthocyanins.Aurones_LegendAndRate$rate.mat
Anthocyanins.Aurones.ind
Anthocyanins.Aurones.ind <- equateStateMatPars(Anthocyanins.Aurones.ind, c(1,6))
Anthocyanins.Aurones.ind
Anthocyanins.Aurones.ind <- equateStateMatPars(Anthocyanins.Aurones.ind, c(1,3))
Anthocyanins.Aurones.ind
Anthocyanins.Aurones.ind <- equateStateMatPars(Anthocyanins.Aurones.ind, c(1,4))
Anthocyanins.Aurones.ind
Anthocyanins.Aurones.ind <- equateStateMatPars(Anthocyanins.Aurones.ind, c(1,2))
Anthocyanins.Aurones.ind

Anthocyanins.Aurones_LegendAndRate <- getStateMat4Dat(Anthocyanins.Aurones) 
Anthocyanins.Aurones_LegendAndRate
Anthocyanins.Aurones.x <- Anthocyanins.Aurones_LegendAndRate$rate.mat
Anthocyanins.Aurones.x
Anthocyanins.Aurones.x <- equateStateMatPars(Anthocyanins.Aurones.x, c(1,6))
Anthocyanins.Aurones.x
Anthocyanins.Aurones.x <- equateStateMatPars(Anthocyanins.Aurones.x, c(2,6))
Anthocyanins.Aurones.x

Anthocyanins.Aurones_LegendAndRate <- getStateMat4Dat(Anthocyanins.Aurones) 
Anthocyanins.Aurones_LegendAndRate
Anthocyanins.Aurones.y <- Anthocyanins.Aurones_LegendAndRate$rate.mat
Anthocyanins.Aurones.y
Anthocyanins.Aurones.y <- equateStateMatPars(Anthocyanins.Aurones.y, c(2,4))
Anthocyanins.Aurones.y
Anthocyanins.Aurones.y <- equateStateMatPars(Anthocyanins.Aurones.y, c(3,5))
Anthocyanins.Aurones.y

RateClassMat <- getRateCatMat(2)
RateClassMat
StateMats <- list(Anthocyanins.Aurones.ind, Anthocyanins.Aurones.ind)
StateMats
IND2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Anthocyanins.Aurones.x, Anthocyanins.Aurones.x)
StateMats
ARDx2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Anthocyanins.Aurones.y, Anthocyanins.Aurones.y)
StateMats
ARDy2 <- getFullMat(StateMats, RateClassMat)

pp.Anthocyanins.Aurones.ARD.1<-corHMM(tree,Anthocyanins.Aurones,rate.cat=1,node.states="marginal")
pp.Anthocyanins.Aurones.ARD.1
plotMKmodel(pp.Anthocyanins.Aurones.ARD.1)
pp.Anthocyanins.Aurones.ER.1<-corHMM(tree,Anthocyanins.Aurones,rate.cat=1, model = "ER", node.states="marginal")
pp.Anthocyanins.Aurones.ER.1
plotMKmodel(pp.Anthocyanins.Aurones.ER.1)
pp.Anthocyanins.Aurones.IND.1<-corHMM(tree,Anthocyanins.Aurones,rate.cat=1,rate.mat=Anthocyanins.Aurones.ind, node.states="marginal")
pp.Anthocyanins.Aurones.IND.1
plotMKmodel(pp.Anthocyanins.Aurones.IND.1)
pp.Anthocyanins.Aurones.ARDx.1<-corHMM(tree,Anthocyanins.Aurones,rate.cat=1,rate.mat=Anthocyanins.Aurones.x, node.states="marginal")
pp.Anthocyanins.Aurones.ARDx.1
plotMKmodel(pp.Anthocyanins.Aurones.ARDx.1)
pp.Anthocyanins.Aurones.ARDy.1<-corHMM(tree,Anthocyanins.Aurones,rate.cat=1,rate.mat=Anthocyanins.Aurones.y, node.states="marginal")
pp.Anthocyanins.Aurones.ARDy.1
plotMKmodel(pp.Anthocyanins.Aurones.ARDy.1)

pp.Anthocyanins.Aurones.ARD.2<-corHMM(tree,Anthocyanins.Aurones,rate.cat=2,node.states="marginal")
pp.Anthocyanins.Aurones.ARD.2
pp.Anthocyanins.Aurones.ER.2<-corHMM(tree,Anthocyanins.Aurones,rate.cat=2, model = "ER", node.states="marginal")
pp.Anthocyanins.Aurones.ER.2

pp.Anthocyanins.Aurones.IND.2<-corHMM(tree,Anthocyanins.Aurones,rate.cat=2,rate.mat=IND2, node.states="marginal")
pp.Anthocyanins.Aurones.IND.2

pp.Anthocyanins.Aurones.ARDx.2<-corHMM(tree,Anthocyanins.Aurones,rate.cat=2,rate.mat=ARDx2, node.states="marginal")
pp.Anthocyanins.Aurones.ARDx.2

pp.Anthocyanins.Aurones.ARDy.2<-corHMM(tree,Anthocyanins.Aurones,rate.cat=2,rate.mat=ARDy2, node.states="marginal")
pp.Anthocyanins.Aurones.ARDy.2

simmap.Anthocyanins.Aurones <- makeSimmap(tree=tree, data=Anthocyanins.Aurones, model=pp.Anthocyanins.Aurones.ARDy.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Anthocyanins.Aurones)

pdffn = paste0("Model.Anthocyanins.Aurones2rates.ARDy.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Anthocyanins.Aurones.ARDy.2)
dev.off()

pdffn = paste0("Anthocyanins.Aurones2rates.ARDy.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Anthocyanins.Aurones.ARDy.2$states,cex=0.5, pie.cex=0.5,title="Anthocyanins.Aurones 2 rates ARDy")
dev.off()

cols<-setNames(c("white","lightgrey","darkgrey", "black", "red","darkorange","orange", "yellow"),levels(c("(0_0,R1)", "(0_0,R2)", "(0_1,R1)", "(0_1,R2)", "(1_0,R1)", "(1_0,R2)", "(1_1,R1)", "(1_1,R2)")))
pdffn = paste0("Anthocyanins.Aurones2ratesfanARDy.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Anthocyanins.Aurones.ARDy.2$states,piecol=cols,cex=0.2)
dev.off()


#Anthocyanins.Carotenoids
Anthocyanins.Carotenoids <- cbind (as.character(mydata[,12][!is.na(mydata[,7]) & !is.na(mydata[,9])]),mydata[,7][!is.na(mydata[,7])& !is.na(mydata[,9])],mydata[,9][!is.na(mydata[,7])& !is.na(mydata[,9])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Anthocyanins.Carotenoids[,1])
tree <- drop.tip(tree, tipstoremove)

Anthocyanins.Carotenoids_LegendAndRate <- getStateMat4Dat(Anthocyanins.Carotenoids) 
Anthocyanins.Carotenoids_LegendAndRate
Anthocyanins.Carotenoids.ind <- Anthocyanins.Carotenoids_LegendAndRate$rate.mat
Anthocyanins.Carotenoids.ind
Anthocyanins.Carotenoids.ind <- equateStateMatPars(Anthocyanins.Carotenoids.ind, c(1,6))
Anthocyanins.Carotenoids.ind
Anthocyanins.Carotenoids.ind <- equateStateMatPars(Anthocyanins.Carotenoids.ind, c(1,3))
Anthocyanins.Carotenoids.ind
Anthocyanins.Carotenoids.ind <- equateStateMatPars(Anthocyanins.Carotenoids.ind, c(1,4))
Anthocyanins.Carotenoids.ind
Anthocyanins.Carotenoids.ind <- equateStateMatPars(Anthocyanins.Carotenoids.ind, c(1,2))
Anthocyanins.Carotenoids.ind

Anthocyanins.Carotenoids_LegendAndRate <- getStateMat4Dat(Anthocyanins.Carotenoids) 
Anthocyanins.Carotenoids_LegendAndRate
Anthocyanins.Carotenoids.x <- Anthocyanins.Carotenoids_LegendAndRate$rate.mat
Anthocyanins.Carotenoids.x
Anthocyanins.Carotenoids.x <- equateStateMatPars(Anthocyanins.Carotenoids.x, c(1,6))
Anthocyanins.Carotenoids.x
Anthocyanins.Carotenoids.x <- equateStateMatPars(Anthocyanins.Carotenoids.x, c(2,6))
Anthocyanins.Carotenoids.x

Anthocyanins.Carotenoids_LegendAndRate <- getStateMat4Dat(Anthocyanins.Carotenoids) 
Anthocyanins.Carotenoids_LegendAndRate
Anthocyanins.Carotenoids.y <- Anthocyanins.Carotenoids_LegendAndRate$rate.mat
Anthocyanins.Carotenoids.y
Anthocyanins.Carotenoids.y <- equateStateMatPars(Anthocyanins.Carotenoids.y, c(2,4))
Anthocyanins.Carotenoids.y
Anthocyanins.Carotenoids.y <- equateStateMatPars(Anthocyanins.Carotenoids.y, c(3,5))
Anthocyanins.Carotenoids.y

RateClassMat <- getRateCatMat(2)
RateClassMat
StateMats <- list(Anthocyanins.Carotenoids.ind, Anthocyanins.Carotenoids.ind)
StateMats
IND2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Anthocyanins.Carotenoids.x, Anthocyanins.Carotenoids.x)
StateMats
ARDx2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Anthocyanins.Carotenoids.y, Anthocyanins.Carotenoids.y)
StateMats
ARDy2 <- getFullMat(StateMats, RateClassMat)

pp.Anthocyanins.Carotenoids.ARD.1<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=1,node.states="marginal")
pp.Anthocyanins.Carotenoids.ARD.1
plotMKmodel(pp.Anthocyanins.Carotenoids.ARD.1)
pp.Anthocyanins.Carotenoids.ER.1<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=1, model = "ER", node.states="marginal")
pp.Anthocyanins.Carotenoids.ER.1
plotMKmodel(pp.Anthocyanins.Carotenoids.ER.1)
pp.Anthocyanins.Carotenoids.IND.1<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=1,rate.mat=Anthocyanins.Carotenoids.ind, node.states="marginal")
pp.Anthocyanins.Carotenoids.IND.1
plotMKmodel(pp.Anthocyanins.Carotenoids.IND.1)
pp.Anthocyanins.Carotenoids.ARDx.1<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=1,rate.mat=Anthocyanins.Carotenoids.x, node.states="marginal")
pp.Anthocyanins.Carotenoids.ARDx.1
plotMKmodel(pp.Anthocyanins.Carotenoids.ARDx.1)
pp.Anthocyanins.Carotenoids.ARDy.1<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=1,rate.mat=Anthocyanins.Carotenoids.y, node.states="marginal")
pp.Anthocyanins.Carotenoids.ARDy.1
plotMKmodel(pp.Anthocyanins.Carotenoids.ARDy.1)

pp.Anthocyanins.Carotenoids.ARD.2<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=2,node.states="marginal")
pp.Anthocyanins.Carotenoids.ARD.2
pp.Anthocyanins.Carotenoids.ER.2<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=2, model = "ER", node.states="marginal")
pp.Anthocyanins.Carotenoids.ER.2

pp.Anthocyanins.Carotenoids.IND.2<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=2,rate.mat=IND2, node.states="marginal")
pp.Anthocyanins.Carotenoids.IND.2

pp.Anthocyanins.Carotenoids.ARDx.2<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=2,rate.mat=ARDx2, node.states="marginal")
pp.Anthocyanins.Carotenoids.ARDx.2

pp.Anthocyanins.Carotenoids.ARDy.2<-corHMM(tree,Anthocyanins.Carotenoids,rate.cat=2,rate.mat=ARDy2, node.states="marginal")
pp.Anthocyanins.Carotenoids.ARDy.2

simmap.Anthocyanins.Carotenoids <- makeSimmap(tree=tree, data=Anthocyanins.Carotenoids, model=pp.Anthocyanins.Carotenoids.ARDx.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Anthocyanins.Carotenoids)

pdffn = paste0("Model.Anthocyanins.Carotenoids2rates.ARDx.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Anthocyanins.Carotenoids.ARDx.2)
dev.off()

pdffn = paste0("Anthocyanins.Carotenoids2rates.ARDx.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Anthocyanins.Carotenoids.ARDx.2$states,cex=0.5, pie.cex=0.5,title="Anthocyanins.Carotenoids 2 rates ARDx")
dev.off()

cols<-setNames(c("white","lightgrey","darkgrey", "black", "red","darkorange","orange", "yellow"),levels(c("(0_0,R1)", "(0_0,R2)", "(0_1,R1)", "(0_1,R2)", "(1_0,R1)", "(1_0,R2)", "(1_1,R1)", "(1_1,R2)")))
pdffn = paste0("Anthocyanins.Carotenoids2ratesfanARDx.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Anthocyanins.Carotenoids.ARDx.2$states,piecol=cols,cex=0.2)
dev.off()


#Anthocyanins.Chlorophylls
Anthocyanins.Chlorophylls <- cbind (as.character(mydata[,12][!is.na(mydata[,7]) & !is.na(mydata[,10])]),mydata[,7][!is.na(mydata[,7])& !is.na(mydata[,10])],mydata[,10][!is.na(mydata[,7])& !is.na(mydata[,10])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Anthocyanins.Chlorophylls[,1])
tree <- drop.tip(tree, tipstoremove)

Anthocyanins.Chlorophylls_LegendAndRate <- getStateMat4Dat(Anthocyanins.Chlorophylls) 
Anthocyanins.Chlorophylls_LegendAndRate
Anthocyanins.Chlorophylls.ind <- Anthocyanins.Chlorophylls_LegendAndRate$rate.mat
Anthocyanins.Chlorophylls.ind
Anthocyanins.Chlorophylls.ind <- equateStateMatPars(Anthocyanins.Chlorophylls.ind, c(1,6))
Anthocyanins.Chlorophylls.ind
Anthocyanins.Chlorophylls.ind <- equateStateMatPars(Anthocyanins.Chlorophylls.ind, c(1,3))
Anthocyanins.Chlorophylls.ind
Anthocyanins.Chlorophylls.ind <- equateStateMatPars(Anthocyanins.Chlorophylls.ind, c(1,4))
Anthocyanins.Chlorophylls.ind
Anthocyanins.Chlorophylls.ind <- equateStateMatPars(Anthocyanins.Chlorophylls.ind, c(1,2))
Anthocyanins.Chlorophylls.ind

Anthocyanins.Chlorophylls_LegendAndRate <- getStateMat4Dat(Anthocyanins.Chlorophylls) 
Anthocyanins.Chlorophylls_LegendAndRate
Anthocyanins.Chlorophylls.x <- Anthocyanins.Chlorophylls_LegendAndRate$rate.mat
Anthocyanins.Chlorophylls.x
Anthocyanins.Chlorophylls.x <- equateStateMatPars(Anthocyanins.Chlorophylls.x, c(1,6))
Anthocyanins.Chlorophylls.x
Anthocyanins.Chlorophylls.x <- equateStateMatPars(Anthocyanins.Chlorophylls.x, c(2,6))
Anthocyanins.Chlorophylls.x

Anthocyanins.Chlorophylls_LegendAndRate <- getStateMat4Dat(Anthocyanins.Chlorophylls) 
Anthocyanins.Chlorophylls_LegendAndRate
Anthocyanins.Chlorophylls.y <- Anthocyanins.Chlorophylls_LegendAndRate$rate.mat
Anthocyanins.Chlorophylls.y
Anthocyanins.Chlorophylls.y <- equateStateMatPars(Anthocyanins.Chlorophylls.y, c(2,4))
Anthocyanins.Chlorophylls.y
Anthocyanins.Chlorophylls.y <- equateStateMatPars(Anthocyanins.Chlorophylls.y, c(3,5))
Anthocyanins.Chlorophylls.y

RateClassMat <- getRateCatMat(2)
RateClassMat
StateMats <- list(Anthocyanins.Chlorophylls.ind, Anthocyanins.Chlorophylls.ind)
StateMats
IND2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Anthocyanins.Chlorophylls.x, Anthocyanins.Chlorophylls.x)
StateMats
ARDx2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Anthocyanins.Chlorophylls.y, Anthocyanins.Chlorophylls.y)
StateMats
ARDy2 <- getFullMat(StateMats, RateClassMat)

pp.Anthocyanins.Chlorophylls.ARD.1<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=1,node.states="marginal")
pp.Anthocyanins.Chlorophylls.ARD.1
plotMKmodel(pp.Anthocyanins.Chlorophylls.ARD.1)
pp.Anthocyanins.Chlorophylls.ER.1<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=1, model = "ER", node.states="marginal")
pp.Anthocyanins.Chlorophylls.ER.1
plotMKmodel(pp.Anthocyanins.Chlorophylls.ER.1)
pp.Anthocyanins.Chlorophylls.IND.1<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=1,rate.mat=Anthocyanins.Chlorophylls.ind, node.states="marginal")
pp.Anthocyanins.Chlorophylls.IND.1
plotMKmodel(pp.Anthocyanins.Chlorophylls.IND.1)
pp.Anthocyanins.Chlorophylls.ARDx.1<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=1,rate.mat=Anthocyanins.Chlorophylls.x, node.states="marginal")
pp.Anthocyanins.Chlorophylls.ARDx.1
plotMKmodel(pp.Anthocyanins.Chlorophylls.ARDx.1)
pp.Anthocyanins.Chlorophylls.ARDy.1<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=1,rate.mat=Anthocyanins.Chlorophylls.y, node.states="marginal")
pp.Anthocyanins.Chlorophylls.ARDy.1
plotMKmodel(pp.Anthocyanins.Chlorophylls.ARDy.1)

pp.Anthocyanins.Chlorophylls.ARD.2<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=2,node.states="marginal")
pp.Anthocyanins.Chlorophylls.ARD.2
pp.Anthocyanins.Chlorophylls.ER.2<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=2, model = "ER", node.states="marginal")
pp.Anthocyanins.Chlorophylls.ER.2

pp.Anthocyanins.Chlorophylls.IND.2<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=2,rate.mat=IND2, node.states="marginal")
pp.Anthocyanins.Chlorophylls.IND.2

pp.Anthocyanins.Chlorophylls.ARDx.2<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=2,rate.mat=ARDx2, node.states="marginal")
pp.Anthocyanins.Chlorophylls.ARDx.2

pp.Anthocyanins.Chlorophylls.ARDy.2<-corHMM(tree,Anthocyanins.Chlorophylls,rate.cat=2,rate.mat=ARDy2, node.states="marginal")
pp.Anthocyanins.Chlorophylls.ARDy.2

simmap.Anthocyanins.Chlorophylls <- makeSimmap(tree=tree, data=Anthocyanins.Chlorophylls, model=pp.Anthocyanins.Chlorophylls.ARD.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Anthocyanins.Chlorophylls)

pdffn = paste0("Model.Anthocyanins.Chlorophylls2rates.ARD.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Anthocyanins.Chlorophylls.ARD.2)
dev.off()

pdffn = paste0("Anthocyanins.Chlorophylls2rates.ARD.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Anthocyanins.Chlorophylls.ARD.2$states,cex=0.5, pie.cex=0.5,title="Anthocyanins.Chlorophylls 2 rates ARD")
dev.off()

cols<-setNames(c("white","lightgrey","darkgrey", "black", "red","darkorange","orange", "yellow"),levels(c("(0_0,R1)", "(0_0,R2)", "(0_1,R1)", "(0_1,R2)", "(1_0,R1)", "(1_0,R2)", "(1_1,R1)", "(1_1,R2)")))
pdffn = paste0("Anthocyanins.Chlorophylls2ratesfanARD.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Anthocyanins.Chlorophylls.ARD.2$states,piecol=cols,cex=0.2)
dev.off()


#Carotenoids.Aurones
Carotenoids.Aurones <- cbind (as.character(mydata[,12][!is.na(mydata[,9]) & !is.na(mydata[,8])]),mydata[,9][!is.na(mydata[,9])& !is.na(mydata[,8])],mydata[,8][!is.na(mydata[,9])& !is.na(mydata[,8])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Carotenoids.Aurones[,1])
tree <- drop.tip(tree, tipstoremove)

Carotenoids.Aurones_LegendAndRate <- getStateMat4Dat(Carotenoids.Aurones) 
Carotenoids.Aurones_LegendAndRate
Carotenoids.Aurones.ind <- Carotenoids.Aurones_LegendAndRate$rate.mat
Carotenoids.Aurones.ind
Carotenoids.Aurones.ind <- equateStateMatPars(Carotenoids.Aurones.ind, c(1,6))
Carotenoids.Aurones.ind
Carotenoids.Aurones.ind <- equateStateMatPars(Carotenoids.Aurones.ind, c(1,3))
Carotenoids.Aurones.ind
Carotenoids.Aurones.ind <- equateStateMatPars(Carotenoids.Aurones.ind, c(1,4))
Carotenoids.Aurones.ind
Carotenoids.Aurones.ind <- equateStateMatPars(Carotenoids.Aurones.ind, c(1,2))
Carotenoids.Aurones.ind

Carotenoids.Aurones_LegendAndRate <- getStateMat4Dat(Carotenoids.Aurones) 
Carotenoids.Aurones_LegendAndRate
Carotenoids.Aurones.x <- Carotenoids.Aurones_LegendAndRate$rate.mat
Carotenoids.Aurones.x
Carotenoids.Aurones.x <- equateStateMatPars(Carotenoids.Aurones.x, c(1,6))
Carotenoids.Aurones.x
Carotenoids.Aurones.x <- equateStateMatPars(Carotenoids.Aurones.x, c(2,6))
Carotenoids.Aurones.x

Carotenoids.Aurones_LegendAndRate <- getStateMat4Dat(Carotenoids.Aurones) 
Carotenoids.Aurones_LegendAndRate
Carotenoids.Aurones.y <- Carotenoids.Aurones_LegendAndRate$rate.mat
Carotenoids.Aurones.y
Carotenoids.Aurones.y <- equateStateMatPars(Carotenoids.Aurones.y, c(2,4))
Carotenoids.Aurones.y
Carotenoids.Aurones.y <- equateStateMatPars(Carotenoids.Aurones.y, c(3,5))
Carotenoids.Aurones.y

RateClassMat <- getRateCatMat(2)
RateClassMat
StateMats <- list(Carotenoids.Aurones.ind, Carotenoids.Aurones.ind)
StateMats
IND2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Carotenoids.Aurones.x, Carotenoids.Aurones.x)
StateMats
ARDx2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Carotenoids.Aurones.y, Carotenoids.Aurones.y)
StateMats
ARDy2 <- getFullMat(StateMats, RateClassMat)

pp.Carotenoids.Aurones.ARD.1<-corHMM(tree,Carotenoids.Aurones,rate.cat=1,node.states="marginal")
pp.Carotenoids.Aurones.ARD.1
plotMKmodel(pp.Carotenoids.Aurones.ARD.1)
pp.Carotenoids.Aurones.ER.1<-corHMM(tree,Carotenoids.Aurones,rate.cat=1, model = "ER", node.states="marginal")
pp.Carotenoids.Aurones.ER.1
plotMKmodel(pp.Carotenoids.Aurones.ER.1)
pp.Carotenoids.Aurones.IND.1<-corHMM(tree,Carotenoids.Aurones,rate.cat=1,rate.mat=Carotenoids.Aurones.ind, node.states="marginal")
pp.Carotenoids.Aurones.IND.1
plotMKmodel(pp.Carotenoids.Aurones.IND.1)
pp.Carotenoids.Aurones.ARDx.1<-corHMM(tree,Carotenoids.Aurones,rate.cat=1,rate.mat=Carotenoids.Aurones.x, node.states="marginal")
pp.Carotenoids.Aurones.ARDx.1
plotMKmodel(pp.Carotenoids.Aurones.ARDx.1)
pp.Carotenoids.Aurones.ARDy.1<-corHMM(tree,Carotenoids.Aurones,rate.cat=1,rate.mat=Carotenoids.Aurones.y, node.states="marginal")
pp.Carotenoids.Aurones.ARDy.1
plotMKmodel(pp.Carotenoids.Aurones.ARDy.1)

pp.Carotenoids.Aurones.ARD.2<-corHMM(tree,Carotenoids.Aurones,rate.cat=2,node.states="marginal")
pp.Carotenoids.Aurones.ARD.2
pp.Carotenoids.Aurones.ER.2<-corHMM(tree,Carotenoids.Aurones,rate.cat=2, model = "ER", node.states="marginal")
pp.Carotenoids.Aurones.ER.2

pp.Carotenoids.Aurones.IND.2<-corHMM(tree,Carotenoids.Aurones,rate.cat=2,rate.mat=IND2, node.states="marginal")
pp.Carotenoids.Aurones.IND.2

pp.Carotenoids.Aurones.ARDx.2<-corHMM(tree,Carotenoids.Aurones,rate.cat=2,rate.mat=ARDx2, node.states="marginal")
pp.Carotenoids.Aurones.ARDx.2

pp.Carotenoids.Aurones.ARDy.2<-corHMM(tree,Carotenoids.Aurones,rate.cat=2,rate.mat=ARDy2, node.states="marginal")
pp.Carotenoids.Aurones.ARDy.2

simmap.Carotenoids.Aurones <- makeSimmap(tree=tree, data=Carotenoids.Aurones, model=pp.Carotenoids.Aurones.IND.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Carotenoids.Aurones)

pdffn = paste0("Model.Carotenoids.Aurones2rates.IND.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Carotenoids.Aurones.IND.2)
dev.off()

pdffn = paste0("Carotenoids.Aurones2rates.IND.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Carotenoids.Aurones.IND.2$states,cex=0.5, pie.cex=0.5,title="Carotenoids.Aurones 2 rates IND")
dev.off()

cols<-setNames(c("white","lightgrey","darkgrey", "black", "red","darkorange","orange", "yellow"),levels(c("(0_0,R1)", "(0_0,R2)", "(0_1,R1)", "(0_1,R2)", "(1_0,R1)", "(1_0,R2)", "(1_1,R1)", "(1_1,R2)")))
pdffn = paste0("Carotenoids.Aurones2ratesfanIND.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Carotenoids.Aurones.IND.2$states,piecol=cols,cex=0.2)
dev.off()


#Carotenoids.Chlorophylls
Carotenoids.Chlorophylls <- cbind (as.character(mydata[,12][!is.na(mydata[,9]) & !is.na(mydata[,10])]),mydata[,9][!is.na(mydata[,9])& !is.na(mydata[,10])],mydata[,10][!is.na(mydata[,9])& !is.na(mydata[,10])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Carotenoids.Chlorophylls[,1])
tree <- drop.tip(tree, tipstoremove)

Carotenoids.Chlorophylls_LegendAndRate <- getStateMat4Dat(Carotenoids.Chlorophylls) 
Carotenoids.Chlorophylls_LegendAndRate
Carotenoids.Chlorophylls.ind <- Carotenoids.Chlorophylls_LegendAndRate$rate.mat
Carotenoids.Chlorophylls.ind
Carotenoids.Chlorophylls.ind <- equateStateMatPars(Carotenoids.Chlorophylls.ind, c(1,6))
Carotenoids.Chlorophylls.ind
Carotenoids.Chlorophylls.ind <- equateStateMatPars(Carotenoids.Chlorophylls.ind, c(1,3))
Carotenoids.Chlorophylls.ind
Carotenoids.Chlorophylls.ind <- equateStateMatPars(Carotenoids.Chlorophylls.ind, c(1,4))
Carotenoids.Chlorophylls.ind
Carotenoids.Chlorophylls.ind <- equateStateMatPars(Carotenoids.Chlorophylls.ind, c(1,2))
Carotenoids.Chlorophylls.ind

Carotenoids.Chlorophylls_LegendAndRate <- getStateMat4Dat(Carotenoids.Chlorophylls) 
Carotenoids.Chlorophylls_LegendAndRate
Carotenoids.Chlorophylls.x <- Carotenoids.Chlorophylls_LegendAndRate$rate.mat
Carotenoids.Chlorophylls.x
Carotenoids.Chlorophylls.x <- equateStateMatPars(Carotenoids.Chlorophylls.x, c(1,6))
Carotenoids.Chlorophylls.x
Carotenoids.Chlorophylls.x <- equateStateMatPars(Carotenoids.Chlorophylls.x, c(2,6))
Carotenoids.Chlorophylls.x

Carotenoids.Chlorophylls_LegendAndRate <- getStateMat4Dat(Carotenoids.Chlorophylls) 
Carotenoids.Chlorophylls_LegendAndRate
Carotenoids.Chlorophylls.y <- Carotenoids.Chlorophylls_LegendAndRate$rate.mat
Carotenoids.Chlorophylls.y
Carotenoids.Chlorophylls.y <- equateStateMatPars(Carotenoids.Chlorophylls.y, c(2,4))
Carotenoids.Chlorophylls.y
Carotenoids.Chlorophylls.y <- equateStateMatPars(Carotenoids.Chlorophylls.y, c(3,5))
Carotenoids.Chlorophylls.y

RateClassMat <- getRateCatMat(2)
RateClassMat
StateMats <- list(Carotenoids.Chlorophylls.ind, Carotenoids.Chlorophylls.ind)
StateMats
IND2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Carotenoids.Chlorophylls.x, Carotenoids.Chlorophylls.x)
StateMats
ARDx2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Carotenoids.Chlorophylls.y, Carotenoids.Chlorophylls.y)
StateMats
ARDy2 <- getFullMat(StateMats, RateClassMat)

pp.Carotenoids.Chlorophylls.ARD.1<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=1,node.states="marginal")
pp.Carotenoids.Chlorophylls.ARD.1
plotMKmodel(pp.Carotenoids.Chlorophylls.ARD.1)
pp.Carotenoids.Chlorophylls.ER.1<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=1, model = "ER", node.states="marginal")
pp.Carotenoids.Chlorophylls.ER.1
plotMKmodel(pp.Carotenoids.Chlorophylls.ER.1)
pp.Carotenoids.Chlorophylls.IND.1<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=1,rate.mat=Carotenoids.Chlorophylls.ind, node.states="marginal")
pp.Carotenoids.Chlorophylls.IND.1
plotMKmodel(pp.Carotenoids.Chlorophylls.IND.1)
pp.Carotenoids.Chlorophylls.ARDx.1<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=1,rate.mat=Carotenoids.Chlorophylls.x, node.states="marginal")
pp.Carotenoids.Chlorophylls.ARDx.1
plotMKmodel(pp.Carotenoids.Chlorophylls.ARDx.1)
pp.Carotenoids.Chlorophylls.ARDy.1<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=1,rate.mat=Carotenoids.Chlorophylls.y, node.states="marginal")
pp.Carotenoids.Chlorophylls.ARDy.1
plotMKmodel(pp.Carotenoids.Chlorophylls.ARDy.1)

pp.Carotenoids.Chlorophylls.ARD.2<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=2,node.states="marginal")
pp.Carotenoids.Chlorophylls.ARD.2
pp.Carotenoids.Chlorophylls.ER.2<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=2, model = "ER", node.states="marginal")
pp.Carotenoids.Chlorophylls.ER.2

pp.Carotenoids.Chlorophylls.IND.2<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=2,rate.mat=IND2, node.states="marginal")
pp.Carotenoids.Chlorophylls.IND.2

pp.Carotenoids.Chlorophylls.ARDx.2<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=2,rate.mat=ARDx2, node.states="marginal")
pp.Carotenoids.Chlorophylls.ARDx.2

pp.Carotenoids.Chlorophylls.ARDy.2<-corHMM(tree,Carotenoids.Chlorophylls,rate.cat=2,rate.mat=ARDy2, node.states="marginal")
pp.Carotenoids.Chlorophylls.ARDy.2

simmap.Carotenoids.Chlorophylls <- makeSimmap(tree=tree, data=Carotenoids.Chlorophylls, model=pp.Carotenoids.Chlorophylls.ARDy.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Carotenoids.Chlorophylls)

pdffn = paste0("Model.Carotenoids.Chlorophylls2rates.ARDy.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Carotenoids.Chlorophylls.ARDy.2)
dev.off()

pdffn = paste0("Carotenoids.Chlorophylls2rates.ARDy.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Carotenoids.Chlorophylls.ARDy.2$states,cex=0.5, pie.cex=0.5,title="Carotenoids.Chlorophylls 2 rates ARDy")
dev.off()

cols<-setNames(c("white","lightgrey","darkgrey", "black", "red","darkorange","orange", "yellow"),levels(c("(0_0,R1)", "(0_0,R2)", "(0_1,R1)", "(0_1,R2)", "(1_0,R1)", "(1_0,R2)", "(1_1,R1)", "(1_1,R2)")))
pdffn = paste0("Carotenoids.Chlorophylls2ratesfanARDy.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Carotenoids.Chlorophylls.ARDy.2$states,piecol=cols,cex=0.2)
dev.off()

#Aurones.Chlorophylls
Aurones.Chlorophylls <- cbind (as.character(mydata[,12][!is.na(mydata[,8]) & !is.na(mydata[,10])]),mydata[,8][!is.na(mydata[,8])& !is.na(mydata[,10])],mydata[,10][!is.na(mydata[,8])& !is.na(mydata[,10])])
library(phytools)
tree <- multi2di(mytree$scenario.2)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Aurones.Chlorophylls[,1])
tree <- drop.tip(tree, tipstoremove)

Aurones.Chlorophylls_LegendAndRate <- getStateMat4Dat(Aurones.Chlorophylls) 
Aurones.Chlorophylls_LegendAndRate
Aurones.Chlorophylls.ind <- Aurones.Chlorophylls_LegendAndRate$rate.mat
Aurones.Chlorophylls.ind
Aurones.Chlorophylls.ind <- equateStateMatPars(Aurones.Chlorophylls.ind, c(1,6))
Aurones.Chlorophylls.ind
Aurones.Chlorophylls.ind <- equateStateMatPars(Aurones.Chlorophylls.ind, c(1,3))
Aurones.Chlorophylls.ind
Aurones.Chlorophylls.ind <- equateStateMatPars(Aurones.Chlorophylls.ind, c(1,4))
Aurones.Chlorophylls.ind
Aurones.Chlorophylls.ind <- equateStateMatPars(Aurones.Chlorophylls.ind, c(1,2))
Aurones.Chlorophylls.ind

Aurones.Chlorophylls_LegendAndRate <- getStateMat4Dat(Aurones.Chlorophylls) 
Aurones.Chlorophylls_LegendAndRate
Aurones.Chlorophylls.x <- Aurones.Chlorophylls_LegendAndRate$rate.mat
Aurones.Chlorophylls.x
Aurones.Chlorophylls.x <- equateStateMatPars(Aurones.Chlorophylls.x, c(1,6))
Aurones.Chlorophylls.x
Aurones.Chlorophylls.x <- equateStateMatPars(Aurones.Chlorophylls.x, c(2,6))
Aurones.Chlorophylls.x

Aurones.Chlorophylls_LegendAndRate <- getStateMat4Dat(Aurones.Chlorophylls) 
Aurones.Chlorophylls_LegendAndRate
Aurones.Chlorophylls.y <- Aurones.Chlorophylls_LegendAndRate$rate.mat
Aurones.Chlorophylls.y
Aurones.Chlorophylls.y <- equateStateMatPars(Aurones.Chlorophylls.y, c(2,4))
Aurones.Chlorophylls.y
Aurones.Chlorophylls.y <- equateStateMatPars(Aurones.Chlorophylls.y, c(3,5))
Aurones.Chlorophylls.y

RateClassMat <- getRateCatMat(2)
RateClassMat
StateMats <- list(Aurones.Chlorophylls.ind, Aurones.Chlorophylls.ind)
StateMats
IND2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Aurones.Chlorophylls.x, Aurones.Chlorophylls.x)
StateMats
ARDx2 <- getFullMat(StateMats, RateClassMat)
StateMats <- list(Aurones.Chlorophylls.y, Aurones.Chlorophylls.y)
StateMats
ARDy2 <- getFullMat(StateMats, RateClassMat)

pp.Aurones.Chlorophylls.ARD.1<-corHMM(tree,Aurones.Chlorophylls,rate.cat=1,node.states="marginal")
pp.Aurones.Chlorophylls.ARD.1
plotMKmodel(pp.Aurones.Chlorophylls.ARD.1)
pp.Aurones.Chlorophylls.ER.1<-corHMM(tree,Aurones.Chlorophylls,rate.cat=1, model = "ER", node.states="marginal")
pp.Aurones.Chlorophylls.ER.1
plotMKmodel(pp.Aurones.Chlorophylls.ER.1)
pp.Aurones.Chlorophylls.IND.1<-corHMM(tree,Aurones.Chlorophylls,rate.cat=1,rate.mat=Aurones.Chlorophylls.ind, node.states="marginal")
pp.Aurones.Chlorophylls.IND.1
plotMKmodel(pp.Aurones.Chlorophylls.IND.1)
pp.Aurones.Chlorophylls.ARDx.1<-corHMM(tree,Aurones.Chlorophylls,rate.cat=1,rate.mat=Aurones.Chlorophylls.x, node.states="marginal")
pp.Aurones.Chlorophylls.ARDx.1
plotMKmodel(pp.Aurones.Chlorophylls.ARDx.1)
pp.Aurones.Chlorophylls.ARDy.1<-corHMM(tree,Aurones.Chlorophylls,rate.cat=1,rate.mat=Aurones.Chlorophylls.y, node.states="marginal")
pp.Aurones.Chlorophylls.ARDy.1
plotMKmodel(pp.Aurones.Chlorophylls.ARDy.1)

pp.Aurones.Chlorophylls.ARD.2<-corHMM(tree,Aurones.Chlorophylls,rate.cat=2,node.states="marginal")
pp.Aurones.Chlorophylls.ARD.2
pp.Aurones.Chlorophylls.ER.2<-corHMM(tree,Aurones.Chlorophylls,rate.cat=2, model = "ER", node.states="marginal")
pp.Aurones.Chlorophylls.ER.2

pp.Aurones.Chlorophylls.IND.2<-corHMM(tree,Aurones.Chlorophylls,rate.cat=2,rate.mat=IND2, node.states="marginal")
pp.Aurones.Chlorophylls.IND.2

pp.Aurones.Chlorophylls.ARDx.2<-corHMM(tree,Aurones.Chlorophylls,rate.cat=2,rate.mat=ARDx2, node.states="marginal")
pp.Aurones.Chlorophylls.ARDx.2

pp.Aurones.Chlorophylls.ARDy.2<-corHMM(tree,Aurones.Chlorophylls,rate.cat=2,rate.mat=ARDy2, node.states="marginal")
pp.Aurones.Chlorophylls.ARDy.2

simmap.Aurones.Chlorophylls <- makeSimmap(tree=tree, data=Aurones.Chlorophylls, model=pp.Aurones.Chlorophylls.IND.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Aurones.Chlorophylls)

pdffn = paste0("Model.Aurones.Chlorophylls2rates.IND.pdf")
pdf(file=pdffn, width=6, height=8)
plotMKmodel(pp.Aurones.Chlorophylls.IND.2)
dev.off()

pdffn = paste0("Aurones.Chlorophylls2rates.IND.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Aurones.Chlorophylls.IND.2$states,cex=0.5, pie.cex=0.5,title="Aurones.Chlorophylls 2 rates IND")
dev.off()

cols<-setNames(c("white","lightgrey","darkgrey", "black", "red","darkorange","orange", "yellow"),levels(c("(0_0,R1)", "(0_0,R2)", "(0_1,R1)", "(0_1,R2)", "(1_0,R1)", "(1_0,R2)", "(1_1,R1)", "(1_1,R2)")))
pdffn = paste0("Aurones.Chlorophylls2ratesfanIND.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Aurones.Chlorophylls.IND.2$states,piecol=cols,cex=0.2)
dev.off()


```


Phylogenetic signal of Anthocyanins
```{r}

#library(geiger)
Anthocyanins[Anthocyanins==0] <- 2
lambda.Anthocyanins <- fitDiscrete(tree, Anthocyanins, model = "ER", transform = "lambda", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Anthocyanins.bm <- fitDiscrete(tree, Anthocyanins, model = "ER", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
tree.lambda <- rescale(tree, "lambda")
tree.lambda(0)
lambda.Anthocyanins.0 <- fitDiscrete(tree.lambda(0), Anthocyanins, model = "ER", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Anthocyanins
lambda.Anthocyanins.bm
lambda.Anthocyanins.0

```



Phylogenetic signal of Aurones
```{r}

#library(geiger)
Aurones[Aurones==0] <- 2
lambda.Aurones <- fitDiscrete(tree, Aurones, model = "ARD", transform = "lambda", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Aurones.bm <- fitDiscrete(tree, Aurones, model = "ARD", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
tree.lambda <- rescale(tree, "lambda")
tree.lambda(0)
lambda.Aurones.0 <- fitDiscrete(tree.lambda(0), Aurones, model = "ARD", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Aurones
lambda.Aurones.bm
lambda.Aurones.0

```


Phylogenetic signal of Carotenoids
```{r}

#library(geiger)
Carotenoids[Carotenoids==0] <- 2
lambda.Carotenoids <- fitDiscrete(tree, Carotenoids, model = "ARD", transform = "lambda", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Carotenoids.bm <- fitDiscrete(tree, Carotenoids, model = "ARD", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
tree.lambda <- rescale(tree, "lambda")
lambda.Carotenoids.0 <- fitDiscrete(tree.lambda(0), Carotenoids, model = "ARD", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Carotenoids
lambda.Carotenoids.bm
lambda.Carotenoids.0
```


Phylogenetic signal of Chlorophylls
```{r}

#library(geiger)
Chlorophylls[Chlorophylls==0] <- 2
lambda.Chlorophylls <- fitDiscrete(tree, Chlorophylls, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Chlorophylls.bm <- fitDiscrete(tree, Chlorophylls, model = "ARD", transform = "none", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
tree.lambda <- rescale(tree, "lambda")
lambda.Chlorophylls.0 <- fitDiscrete(tree.lambda(0), Chlorophylls, model = "ARD", transform = "none", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Chlorophylls
lambda.Chlorophylls.bm
lambda.Chlorophylls.0

```


ML reconstruction number of pigments.

```{r}
library(phytools)

names(mydata)
NPigments <- mydata[,14]
names(NPigments) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

NPigments<-NPigments[!is.na(NPigments)]
tipstoremove <- setdiff(tree$tip.label,names(NPigments))
tree <- drop.tip(tree, tipstoremove)



pdffn = paste0("NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.NPigments<-ace(NPigments, tree,model="ER",type="discrete")
names(fitER.NPigments)

pdffn = paste0("ML_ER_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.NPigments<-ace(NPigments,tree,model="ARD",type="discrete")
fitARD.NPigments
pdffn = paste0("ML_ARD_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitSYM.NPigments<-ace(NPigments,tree,model="SYM",type="discrete")
fitSYM.NPigments
pdffn = paste0("ML_SYM_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitSYM.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

ARDstep <- matrix(c(0, 1, 0, 0, 2, 0, 3, 0, 0, 4, 0, 5, 0, 0, 6, 0), 4)
fitARDstep.NPigments<-ace(NPigments,tree,model=ARDstep,type="discrete")
fitARDstep.NPigments


names(mydata)
Flavonoids <- mydata[,9]
names(Flavonoids) <- mydata[,5]
Flavonoids[Flavonoids==0] <- 2
#Flavonoids[is.na(Flavonoids)] <- "3"
Flavonoids
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Anthocyanins[Anthocyanins==0] <- 2
#Anthocyanins[is.na(Anthocyanins)] <- "3"
Anthocyanins
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]
Aurones[Aurones==0] <- 2
#Aurones[is.na(Aurones)] <- "3"
Aurones
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]
Carotenoids[Carotenoids==0] <- 2
#Carotenoids[is.na(Carotenoids)] <- "3"
Carotenoids
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]
Chlorophylls[Chlorophylls==0] <- 2
#Chlorophylls[is.na(Chlorophylls)] <- "3"
Chlorophylls

#cols<-setNames(c("lightpink","#e75480","purple","#301934"),levels(as.factor(NPigments)))
cols<-setNames(c("white","lightgrey","#555555","black"),levels(as.factor(NPigments)))
cols5<-setNames(c("lightyellow","lightgrey"),levels(as.factor(Flavonoids)))
cols2<-setNames(c("blue","lightgrey"),levels(as.factor(Anthocyanins)))
cols3<-setNames(c("orange","lightgrey"),levels(as.factor(Carotenoids)))
cols4<-setNames(c("#FFCC00","lightgrey"),levels(as.factor(Aurones)))
cols6<-setNames(c("darkgreen","lightgrey"),levels(as.factor(Chlorophylls)))
node1 <- getMRCA(tree, c("Acritopappus_sp","Richterago_arenaria"))
node2 <- getMRCA(tree, c("Orchis_anthropophora","Gomesa_hydrophila"))
node3 <- getMRCA(tree, c("Clinopodium_nepeta","Stachys_ocymastrum"))
node4 <- getMRCA(tree, c("Pedicularis_sylvatica","Cistanche_phelypaea"))
node5 <- getMRCA(tree, c("Silene_adscendens","Paronychia_argentea"))
node6 <- getMRCA(tree, c("Solanum_paniculatum","Evolvulus_lithospermoides"))
node7<- getMRCA(tree, c("Trifolium_fragiferum","Hymenaea_sp"))
node8<- getMRCA(tree, c("Heliotropium_europaeum","Cynoglossum_clandestinum"))
node9<- getMRCA(tree, c("Sisymbrium_austriacum","Malcolmia_littorea"))
node10<- getMRCA(tree, c("Cistus_crispus","Malva_maroccana"))
node11<- getMRCA(tree, c("Nigella_damascena","Papaver_argemone"))
node12<- getMRCA(tree, c("Linum_trigynum","Euphorbia_segetalis"))
node13<- getMRCA(tree, c("Rosa_canina","Crataegus_monogyna"))
node14<- getMRCA(tree, c("Banisteriopsis_campestris","Byrsonima_dealbata"))
node15<- getMRCA(tree, c("Geranium_molle","Erodium_moschatum"))
node16<- getMRCA(tree, c("Cambessedesia_corymbosa","Miconia_rubiginosa"))
node17<- getMRCA(tree, c("Declieuxia_fruticosa","Asperula_hirsuta"))
node18<- getMRCA(tree, c("Cymbalaria_muralis","Linaria_spartea"))
node19<- getMRCA(tree, c("Romulea_bulbocodium","Iris_planifolia"))
node20<- getMRCA(tree, c("Allium_roseum","Acis_autumnalis"))
node21<- getMRCA(tree, c("Scilla_peruviana","Prospero_autumnale"))
node22<- getMRCA(tree, c("Xyris_asperula","Xyris_piranii"))

pdffn = paste0("ML_ARDstep_NPigments.pdf")
pdf(file=pdffn, width=30, height=30)
par(mar = c(0.1, 0.1, 0.1, 0.1))
plot(tree,type="fan",show.tip.label = T, cex = 0.1,  tip.color="white", edge.color = "grey", edge.width = 5, no.margin = F)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols, bg=cols,cex=0.1,offset = 1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARDstep.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=1*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Flavonoids[tree$tip.label],
    levels(as.factor(Flavonoids))),piecol=cols5, bg=cols5,cex=0.1, offset = 2.5)
add.simmap.legend(colors=cols5,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Anthocyanins[tree$tip.label],
    levels(as.factor(Anthocyanins))),piecol=cols2, bg=cols2,cex=0.1, offset = 4)
add.simmap.legend(colors=cols2,prompt=FALSE,x=0.8*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Carotenoids[tree$tip.label],
    levels(as.factor(Carotenoids))),piecol=cols3, bg=cols3,cex=0.1, offset = 5.5)
add.simmap.legend(colors=cols3,prompt=FALSE,x=0.7*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Chlorophylls[tree$tip.label],
    levels(as.factor(Chlorophylls))),piecol=cols6, bg=cols6,cex=0.1, offset = 7)
add.simmap.legend(colors=cols6,prompt=FALSE,x=0.8*par()$usr[1],
    y=0.9*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Aurones[tree$tip.label],
    levels(as.factor(Aurones))),piecol=cols4, bg=cols4,cex=0.1, offset = 8.5)
add.simmap.legend(colors=cols4,prompt=FALSE,x=0.7*par()$usr[1],
    y=0.9*par()$usr[3],fsize=2)
arc.cladelabels(tree, "Asteraceae", node1, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Orchidaceae", node2, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Lamiaceae", node3, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Orobanchaceae", node4, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Caryophyllaceae", node5, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Solanaceae-Convolvulaceae", node6, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Fabaceae", node7, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Boraginaceae", node8, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Brassicaceae", node9, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Malvaceae-Cistaceae", node10, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Papaveraceae-Ranunculaceae", node11, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Linaceae-Euphorbiaceae", node12, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1,orientation="curved", stretch=1)
arc.cladelabels(tree, "Rosaceae", node13, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Malpighiaceae", node14, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Geraniaceae", node15, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Melastomataceae", node16, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Rubiaceae", node17, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Plantaginaceae", node18, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Iridaceae", node19, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Amaryllidaceae", node20, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.8,orientation="curved", stretch=1)
arc.cladelabels(tree, "Asparagaceae", node21, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Xyridaceae", node22, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
dev.off()

```


Stochastic mapping Number of Pigments: This could take very long, we are not goint to do it for now.
```{r}

mtree<-make.simmap(tree,NPigments,model=ARDstep, nsim=1)
mtree
cols<-setNames(c("red","blue", "green", "yellow"),levels(as.factor(NPigments)))

pdffn = paste0("BSM_1map_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset=1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.NPigments<-make.simmap(tree,NPigments,model=ARDstep,nsim=100)


pd.NPigments<-summary(mtrees.NPigments)
pd.NPigments



############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_NPigments_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.NPigments,1)[[1]],cols,fsize=0.6,ftype="i",offset = 1)
nodelabels(pie=pd.NPigments$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[4:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()




```

Phylogenetic signal of NPigments
```{r}

library(geiger)
NPigments[NPigments==0] <- "zero"
lambda.NPigments <- fitDiscrete(tree, NPigments, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.NPigments.bm <- fitDiscrete(tree, NPigments, model = "ARD", transform = "none", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)

tree.lambda <- rescale(tree, "lambda")
tree.lambda(0)
lambda.NPigments.0 <- fitDiscrete(tree.lambda(0), NPigments, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)

lambda.NPigments
lambda.NPigments.bm
lambda.NPigments.0

```



