---
title: "Color y recompensas"
author: "Marcial"
date: "01/09/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---
1. Install and load packages

```{r, echo = F}
#devtools::install_github("jinyizju/V.PhyloMaker")
library(V.PhyloMaker)


```


3. Frequency matrix.

```{r, echo = F}
mydata <- read.csv("./PIGMENT_EVOLUTION_V4.csv") 
dim(mydata)
mydata <- mydata[1:693,1:17]
```



3. Create your tree and plot

```{r, echo = F}



genera<-sapply(strsplit(as.character(mydata[,5]),"_"),function(x) x[1])
epithet<-sapply(strsplit(as.character(mydata[,5]),"_"),function(x) x[2])

library(Taxonstand)
correctednames <- TPL(genus = genera, species = epithet, infrasp = NULL,infra = TRUE, corr = TRUE, diffchar = 2, max.distance = 1,version = "1.1", encoding = "UTF-8", author = TRUE,drop.lower.level = FALSE, file = "", silent = TRUE, repeats = 6)
write.csv(correctednames,"correctednames.csv", row.names = FALSE)


species <- paste(correctednames$New.Genus,correctednames$New.Species, sep = "_")
duplicated(species)

mydata[,5] <- as.character(mydata[,5])
mydata[,5][duplicated(species)]
species[duplicated(species)]
species[duplicated(species)] <- mydata[,5][duplicated(species)]

duplicated(species)

#mydata[,5][duplicated(species, fromLast = TRUE)]
#species[duplicated(species, fromLast = TRUE)]
#species[duplicated(species, fromLast = TRUE)] <- mydata[,5][duplicated(species, fromLast = TRUE)]

#duplicated(species)

loaddata <- data.frame(species = species, genus = correctednames$New.Genus, family = mydata[,3])
my.phylo.maker <- phylo.maker(data, tree = GBOTB.extended, nodes = nodes.info.1, output.sp.list = TRUE, output.tree = FALSE, scenarios = c("S1","S2","S3"), r = 1)


speciesnamesversions <- cbind(as.character(mydata[,5]), paste(correctednames$New.Genus,correctednames$New.Species, sep = "_"), species )

my.phylo.maker$scenario.3$tip.label <- speciesnamesversions[,1][match(my.phylo.maker$scenario.3$tip.label,speciesnamesversions[,3])]
pdffn = paste0("myphylo", ".scenario3.pdf")
pdf(file=pdffn, width=6, height=60)
plot(my.phylo.maker$scenario.3, cex = 0.5)
dev.off()
write.tree(my.phylo.maker$scenario.3, file = "mytree3.tree")

my.phylo.maker$scenario.2$run.1$tip.label <- speciesnamesversions[,1][match(my.phylo.maker$scenario.2$run.1$tip.label,speciesnamesversions[,3])]
pdffn = paste0("myphylo", ".scenario2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(my.phylo.maker$scenario.2$run.1, cex = 0.5)
dev.off()
write.tree(my.phylo.maker$scenario.2$run.1, file = "mytree2.tree")

my.phylo.maker$scenario.1$tip.label <- speciesnamesversions[,1][match(my.phylo.maker$scenario.1$tip.label,speciesnamesversions[,3])]
pdffn = paste0("myphylo", ".scenario1.pdf")
pdf(file=pdffn, width=6, height=60)
plot(my.phylo.maker$scenario.1, cex = 0.5)
dev.off()
write.tree(my.phylo.maker$scenario.1, file = "mytree1.tree")

```


ML reconstruction Anthocyanins

```{r}

names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(Anthocyanins))


pdffn = paste0("Anthocyanins.pdf")
pdf(file=pdffn, width=27, height=27)
plot.phylo(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Anthocyanins[tree$tip.label],
    levels(as.factor(Anthocyanins))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=0.3)
dev.off()

fitER.Anthocyanins<-ace(Anthocyanins, tree,model="ER",type="discrete")
fitER.Anthocyanins

pdffn = paste0("ML_ER_Anthocyanins.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Anthocyanins[tree$tip.label],
    levels(as.factor(Anthocyanins))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.Anthocyanins$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.Anthocyanins<-ace(Anthocyanins,tree,model="ARD",type="discrete")
fitARD.Anthocyanins
pdffn = paste0("ML_ARD_Anthocyanins.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Anthocyanins[tree$tip.label],
    levels(as.factor(Anthocyanins))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.Anthocyanins$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping Anthocyanins
```{r}

mtree<-make.simmap(tree,Anthocyanins,model="ER", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(Anthocyanins)))

pdffn = paste0("BSM_1map_Anthocyanins.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree, cols, type="fan",ftype="i",fsize=0.6, offset=1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=0.8)
dev.off()

mtrees.Anthocyanins<-make.simmap(tree,Anthocyanins,model="ER",nsim=100)


pd.Anthocyanins<-summary(mtrees.Anthocyanins)
pd.Anthocyanins

############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Anthocyanins_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.Anthocyanins,1)[[1]],cols,fsize=0.6,ftype="i", offset = 1)
nodelabels(pie=pd.Anthocyanins$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()


obj.Anthocyanins<-densityMap(mtrees.Anthocyanins,states=levels(as.factor(Anthocyanins))[2:1],plot=FALSE)


############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Anthocyanins_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.Anthocyanins,fsize=c(0.6,1))
dev.off()
```


Phylogenetic signal of Anthocyanins
```{r}

#library(geiger)
Anthocyanins[Anthocyanins==0] <- 2
lambda.Anthocyanins <- fitDiscrete(tree, Anthocyanins, model = "ER", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Anthocyanins

```



ML reconstruction Aurones

```{r}

names(mydata)
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Aurones<-Aurones[!is.na(Aurones)]
tipstoremove <- setdiff(tree$tip.label,names(Aurones))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(as.factor(Aurones)))


pdffn = paste0("Aurones.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Aurones[tree$tip.label],
    levels(as.factor(Aurones))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.Aurones<-ace(Aurones, tree,model="ER",type="discrete")
fitER.Aurones

pdffn = paste0("ML_ER_Aurones.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Aurones[tree$tip.label],
    levels(as.factor(Aurones))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.Aurones$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.Aurones<-ace(Aurones,tree,model="ARD",type="discrete")
fitARD.Aurones
pdffn = paste0("ML_ARD_Aurones.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Aurones[tree$tip.label],
    levels(as.factor(Aurones))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.Aurones$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping Aurones
```{r}

mtree<-make.simmap(tree,Aurones,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(Aurones)))

pdffn = paste0("BSM_1map_Aurones.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,type="fan",cols, fsize=0.6,ftype="i", offset = 1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.Aurones<-make.simmap(tree,Aurones,model="ARD",nsim=100)


pd.Aurones<-summary(mtrees.Aurones)
pd.Aurones


############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Aurones_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.Aurones,1)[[1]],cols,fsize=0.6,ftype="i", offset = 1)
nodelabels(pie=pd.Aurones$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()


obj.Aurones<-densityMap(mtrees.Aurones,states=levels(as.factor(Aurones))[2:1],plot=FALSE)

############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Aurones_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.Aurones,fsize=c(0.6,1))
dev.off()

```


Phylogenetic signal of Aurones
```{r}

#library(geiger)
Aurones[Aurones==0] <- 2
lambda.Aurones <- fitDiscrete(tree, Aurones, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Aurones

```



ML reconstruction Carotenoids

```{r}

names(mydata)
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Carotenoids<-Carotenoids[!is.na(Carotenoids)]
tipstoremove <- setdiff(tree$tip.label,names(Carotenoids))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(as.factor(Carotenoids)))


pdffn = paste0("Carotenoids.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Carotenoids[tree$tip.label],
    levels(as.factor(Carotenoids))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.Carotenoids<-ace(Carotenoids, tree,model="ER",type="discrete")
fitER.Carotenoids

pdffn = paste0("ML_ER_Carotenoids.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Carotenoids[tree$tip.label],
    levels(as.factor(Carotenoids))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.Carotenoids$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.Carotenoids<-ace(Carotenoids,tree,model="ARD",type="discrete")
fitARD.Carotenoids
pdffn = paste0("ML_ARD_Carotenoids.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Carotenoids[tree$tip.label],
    levels(as.factor(Carotenoids))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.Carotenoids$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping Carotenoids
```{r}

mtree<-make.simmap(tree,Carotenoids,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(Carotenoids)))

pdffn = paste0("BSM_1map_Carotenoids.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset = 1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.Carotenoids<-make.simmap(tree,Carotenoids,model="ARD",nsim=100)


pd.Carotenoids<-summary(mtrees.Carotenoids)
pd.Carotenoids


############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Carotenoids_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.Carotenoids,1)[[1]],cols,fsize=0.6,ftype="i", offset = 1)
nodelabels(pie=pd.Carotenoids$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE,fsize=2)
############################################
# Close PDF
############################################
dev.off()


obj.Carotenoids<-densityMap(mtrees.Carotenoids,states=levels(as.factor(Carotenoids))[2:1],plot=FALSE)


############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Carotenoids_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.Carotenoids,fsize=c(0.6,1))
dev.off()

```

Phylogenetic signal of Carotenoids
```{r}

#library(geiger)
Carotenoids[Carotenoids==0] <- 2
lambda.Carotenoids <- fitDiscrete(tree, Carotenoids, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Carotenoids

```


ML reconstruction Chlorophylls

```{r}

names(mydata)
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Chlorophylls<-Chlorophylls[!is.na(Chlorophylls)]
tipstoremove <- setdiff(tree$tip.label,names(Chlorophylls))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(as.factor(Chlorophylls)))


pdffn = paste0("Chlorophylls.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Chlorophylls[tree$tip.label],
    levels(as.factor(Chlorophylls))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.Chlorophylls<-ace(Chlorophylls, tree,model="ER",type="discrete")
fitER.Chlorophylls

pdffn = paste0("ML_ER_Chlorophylls.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Chlorophylls[tree$tip.label],
    levels(as.factor(Chlorophylls))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.Chlorophylls$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.Chlorophylls<-ace(Chlorophylls,tree,model="ARD",type="discrete")
fitARD.Chlorophylls
pdffn = paste0("ML_ARD_Chlorophylls.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Chlorophylls[tree$tip.label],
    levels(as.factor(Chlorophylls))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.Chlorophylls$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping Chlorophylls
```{r}

mtree<-make.simmap(tree,Chlorophylls,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(Chlorophylls)))

pdffn = paste0("BSM_1map_Chlorophylls.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset = 1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.Chlorophylls<-make.simmap(tree,Chlorophylls,model="ARD",nsim=100)


pd.Chlorophylls<-summary(mtrees.Chlorophylls)
pd.Chlorophylls



############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Chlorophylls_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plot(sample(mtrees.Chlorophylls,1)[[1]],cols,fsize=0.6,ftype="i",offset=1)
nodelabels(pie=pd.Chlorophylls$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()


obj.Chlorophylls<-densityMap(mtrees.Chlorophylls,states=levels(as.factor(Chlorophylls))[2:1],plot=FALSE)

############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Chlorophylls_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.Chlorophylls,fsize=c(0.6,1))
dev.off()

```

Phylogenetic signal of Chlorophylls
```{r}

#library(geiger)
Chlorophylls[Chlorophylls==0] <- 2
lambda.Chlorophylls <- fitDiscrete(tree, Chlorophylls, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Chlorophylls

```


ML reconstruction number of pigments.

```{r}

names(mydata)
NPigments <- mydata[,14]
names(NPigments) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

NPigments<-NPigments[!is.na(NPigments)]
tipstoremove <- setdiff(tree$tip.label,names(NPigments))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue","green","yellow"),levels(as.factor(NPigments)))


pdffn = paste0("NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.NPigments<-ace(NPigments, tree,model="ER",type="discrete")
fitER.NPigments

pdffn = paste0("ML_ER_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.NPigments<-ace(NPigments,tree,model="ARD",type="discrete")
fitARD.NPigments
pdffn = paste0("ML_ARD_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitSYM.NPigments<-ace(NPigments,tree,model="SYM",type="discrete")
fitSYM.NPigments
pdffn = paste0("ML_SYM_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitSYM.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()


```


Stochastic mapping Number of Pigments: This could take very long, we are not goint to do it for now.
```{r}

mtree<-make.simmap(tree,NPigments,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue", "green", "yellow"),levels(as.factor(NPigments)))

pdffn = paste0("BSM_1map_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset=1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.NPigments<-make.simmap(tree,NPigments,model="ARD",nsim=100)


pd.NPigments<-summary(mtrees.NPigments)
pd.NPigments



############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_NPigments_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.NPigments,1)[[1]],cols,fsize=0.6,ftype="i",offset = 1)
nodelabels(pie=pd.NPigments$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[4:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()




```

Phylogenetic signal of NPigments
```{r}

#library(geiger)
NPigments[NPigments==0] <- "zero"
lambda.NPigments <- fitDiscrete(tree, NPigments, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.NPigments

```



ML reconstruction BlueFlowers

```{r}

names(mydata)
BlueFlowers <- mydata[,15]
names(BlueFlowers) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

BlueFlowers<-BlueFlowers[!is.na(BlueFlowers)]
tipstoremove <- setdiff(tree$tip.label,names(BlueFlowers))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(as.factor(BlueFlowers)))


pdffn = paste0("BlueFlowers.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(BlueFlowers[tree$tip.label],
    levels(as.factor(BlueFlowers))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.BlueFlowers<-ace(BlueFlowers, tree,model="ER",type="discrete")
fitER.BlueFlowers

pdffn = paste0("ML_ER_BlueFlowers.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(BlueFlowers[tree$tip.label],
    levels(as.factor(BlueFlowers))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.BlueFlowers$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.BlueFlowers<-ace(BlueFlowers,tree,model="ARD",type="discrete")
fitARD.BlueFlowers
pdffn = paste0("ML_ARD_BlueFlowers.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(BlueFlowers[tree$tip.label],
    levels(as.factor(BlueFlowers))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.BlueFlowers$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping BlueFlowers
```{r}

mtree<-make.simmap(tree,BlueFlowers,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(BlueFlowers)))

pdffn = paste0("BSM_1map_BlueFlowers.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset = 1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.BlueFlowers<-make.simmap(tree,BlueFlowers,model="ARD",nsim=100)


pd.BlueFlowers<-summary(mtrees.BlueFlowers)
pd.BlueFlowers



############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_BlueFlowers_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.BlueFlowers,1)[[1]],cols,fsize=0.6,ftype="i", offset = 1)
nodelabels(pie=pd.BlueFlowers$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()


obj.BlueFlowers<-densityMap(mtrees.BlueFlowers,states=levels(as.factor(BlueFlowers))[2:1],plot=FALSE)

############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_BlueFlowers_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.BlueFlowers,fsize=c(0.6,1))
dev.off()

```

Phylogenetic signal of BlueFlowers
```{r}

#library(geiger)
BlueFlowers[BlueFlowers==0] <- 2
lambda.BlueFlowers <- fitDiscrete(tree, BlueFlowers, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.BlueFlowers

```

Dependent or independen evolution

```{r}
library(phytools)

names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
Aurones<-Aurones[!is.na(Aurones)]
setdiff(names(Anthocyanins),names(Aurones))
setdiff(names(Aurones),names(Anthocyanins))
Anthocyanins <- Anthocyanins[which(names(Anthocyanins) %in% names(Aurones))]
Aurones<- Aurones[which(names(Aurones) %in% names(Anthocyanins) )]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)

x <-  Anthocyanins
x[x==0] <- "N.An"
x[x==1] <- "An"
y <- Aurones
y[y==0] <- "N.Au"
y[y==1] <- "Au"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER


names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
Carotenoids<-Carotenoids[!is.na(Carotenoids)]
setdiff(names(Anthocyanins),names(Carotenoids))
setdiff(names(Carotenoids),names(Anthocyanins))
Anthocyanins <- Anthocyanins[which(names(Anthocyanins) %in% names(Carotenoids))]
Carotenoids<- Carotenoids[which(names(Carotenoids) %in% names(Anthocyanins) )]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)

x <-  Anthocyanins
x[x==0] <- "N.An"
x[x==1] <- "An"
y <- Carotenoids
y[y==0] <- "N.Ca"
y[y==1] <- "Ca"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER


names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
Chlorophylls<-Chlorophylls[!is.na(Chlorophylls)]
setdiff(names(Anthocyanins),names(Chlorophylls))
setdiff(names(Chlorophylls),names(Anthocyanins))
Anthocyanins <- Anthocyanins[which(names(Anthocyanins) %in% names(Chlorophylls))]
Chlorophylls<- Chlorophylls[which(names(Chlorophylls) %in% names(Anthocyanins) )]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)

x <-  Anthocyanins
x[x==0] <- "N.An"
x[x==1] <- "An"
y <- Chlorophylls
y[y==0] <- "N.Ch"
y[y==1] <- "Ch"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER


names(mydata)
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Aurones<-Aurones[!is.na(Aurones)]
Carotenoids<-Carotenoids[!is.na(Carotenoids)]
setdiff(names(Aurones),names(Carotenoids))
setdiff(names(Carotenoids),names(Aurones))
Aurones <- Aurones[which(names(Aurones) %in% names(Carotenoids))]
Carotenoids<- Carotenoids[which(names(Carotenoids) %in% names(Aurones) )]
tipstoremove <- setdiff(tree$tip.label,names(Aurones))
tree <- drop.tip(tree, tipstoremove)

x <-  Aurones
x[x==0] <- "N.Au"
x[x==1] <- "Au"
y <- Carotenoids
y[y==0] <- "N.Ca"
y[y==1] <- "Ca"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER
  

names(mydata)
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Aurones<-Aurones[!is.na(Aurones)]
Chlorophylls<-Chlorophylls[!is.na(Chlorophylls)]
setdiff(names(Aurones),names(Chlorophylls))
setdiff(names(Chlorophylls),names(Aurones))
Aurones <- Aurones[which(names(Aurones) %in% names(Chlorophylls))]
Chlorophylls<- Chlorophylls[which(names(Chlorophylls) %in% names(Aurones) )]
tipstoremove <- setdiff(tree$tip.label,names(Aurones))
tree <- drop.tip(tree, tipstoremove)

x <-  Aurones
x[x==0] <- "N.Au"
x[x==1] <- "Au"
y <- Chlorophylls
y[y==0] <- "N.Ch"
y[y==1] <- "Ch"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER


names(mydata)
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Carotenoids<-Carotenoids[!is.na(Carotenoids)]
Chlorophylls<-Chlorophylls[!is.na(Chlorophylls)]
setdiff(names(Carotenoids),names(Chlorophylls))
setdiff(names(Chlorophylls),names(Carotenoids))
Carotenoids <- Carotenoids[which(names(Carotenoids) %in% names(Chlorophylls))]
Chlorophylls<- Chlorophylls[which(names(Chlorophylls) %in% names(Carotenoids) )]
tipstoremove <- setdiff(tree$tip.label,names(Carotenoids))
tree <- drop.tip(tree, tipstoremove)

x <-  Carotenoids
x[x==0] <- "N.Ca"
x[x==1] <- "Ca"
y <- Chlorophylls
y[y==0] <- "N.Ch"
y[y==1] <- "Ch"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER

```


Analyses with corHMM
```{r}

library(corHMM)

names(mydata)
Anthocyanins <- cbind (as.character(mydata[,5][!is.na(mydata[,10])]),mydata[,10][!is.na(mydata[,10])])
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Anthocyanins[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Anthocyanins<-corHMM(tree,Anthocyanins,rate.cat=2,node.states="marginal")
pp.Anthocyanins
pp.Anthocyanins.1<-corHMM(tree,Anthocyanins,rate.cat=1,node.states="marginal")
pp.Anthocyanins.1

pdffn = paste0("Anthocyanins2rates.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Anthocyanins$states,cex=0.5, pie.cex=0.5,title="Anthocyanins 2 rates")
dev.off()

pdffn = paste0("Anthocyanins2rates.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Anthocyanins$states,cex=0.5, pie.cex=0.5,title="Anthocyanins 2 rates")
dev.off()


cols <- c("white", "black", "red", "yellow")
pdffn = paste0("Anthocyanins2ratesfan.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Anthocyanins$states,piecol=cols,cex=0.2)
dev.off()


names(mydata)
Aurones <- cbind (as.character(mydata[,5][!is.na(mydata[,11])]),mydata[,11][!is.na(mydata[,11])])
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Aurones[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Aurones<-corHMM(tree,Aurones,rate.cat=2,node.states="marginal")
pp.Aurones
pp.Aurones.1<-corHMM(tree,Aurones,rate.cat=1,node.states="marginal")
pp.Aurones.1

pdffn = paste0("Aurones2rates.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Aurones$states,cex=0.5, pie.cex=0.5,title="Aurones 2 rates")
dev.off()



cols <- c("white", "black", "red", "yellow")
pdffn = paste0("Aurones2ratesfan.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Aurones$states,piecol=cols,cex=0.2)
dev.off()


names(mydata)
Carotenoids <- cbind (as.character(mydata[,5][!is.na(mydata[,12])]),mydata[,12][!is.na(mydata[,12])])
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Carotenoids[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Carotenoids<-corHMM(tree,Carotenoids,rate.cat=2,node.states="marginal")
pp.Carotenoids
pp.Carotenoids.1<-corHMM(tree,Carotenoids,rate.cat=1,node.states="marginal")
pp.Carotenoids.1

pdffn = paste0("Carotenoids2rates.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Carotenoids$states,cex=0.5, pie.cex=0.5,title="Carotenoids 2 rates")
dev.off()


cols <- c("white", "black", "red", "yellow")
pdffn = paste0("Carotenoids2ratesfan.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Carotenoids$states,piecol=cols,cex=0.2)
dev.off()


names(mydata)
Chlorophylls <- cbind (as.character(mydata[,5][!is.na(mydata[,13])]),mydata[,13][!is.na(mydata[,13])])
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Chlorophylls[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Chlorophylls<-corHMM(tree,Chlorophylls,rate.cat=2,node.states="marginal")
pp.Chlorophylls
pp.Chlorophylls.1<-corHMM(tree,Chlorophylls,rate.cat=1,node.states="marginal")
pp.Chlorophylls.1

pdffn = paste0("Chlorophylls2rates.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Chlorophylls$states,cex=0.5, pie.cex=0.5,title="Chlorophylls 2 rates")
dev.off()


cols <- c("white", "black", "red", "yellow")
pdffn = paste0("Chlorophylls2ratesfan.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Chlorophylls$states,piecol=cols,cex=0.2)
dev.off()
















names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
Aurones<-Aurones[!is.na(Aurones)]
setdiff(names(Anthocyanins),names(Aurones))
setdiff(names(Aurones),names(Anthocyanins))
Anthocyanins <- Anthocyanins[which(names(Anthocyanins) %in% names(Aurones))]
Aurones<- Aurones[which(names(Aurones) %in% names(Anthocyanins) )]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)
Anthocyanins.Aurones <- cbind(names(Anthocyanins), Anthocyanins, Aurones)


#pp.Anthocyanins.Aurones.ER.null<-corDISC(tree,Anthocyanins.Aurones,ntraits=2,model="ER", node.states="marginal")
#pp.Anthocyanins.Aurones.ER.null
#pp.Anthocyanins.Aurones.ARD.null<-corDISC(tree,Anthocyanins.Aurones,ntraits=2,model="ARD", node.states="marginal")
#pp.Anthocyanins.Aurones.ARD.null
#pp.Anthocyanins.Aurones.paint<-corPAINT(tree,Anthocyanins.Aurones,ntraits=2,model=c("ER","ARD"), node.states="marginal")
#pp.Anthocyanins.Aurones.paint
#We need here a column to define the selective regimes!!!!! Ask to Edur

```

