---
title: "Color y recompensas"
author: "Marcial"
date: "01/09/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---
1. Install and load packages

```{r, echo = F}
#library("devtools")
#devtools::install_github("jinyizju/V.PhyloMaker2")
library(V.PhyloMaker2)

# github (requires `remotes` or `devtools`)
#devtools::install_github("ecoinfor/U.Taxonstand")
library(U.Taxonstand)

```


3. Frequency matrix.

```{r, echo = F}
mydata <- read.csv("./PIGMENT_EVOLUTION_V7.csv") 
dim(mydata)
```



3. Create your tree and plot

```{r, echo = F}

# load the database

library(openxlsx)
#dat1 <- read.xlsx("WFO_v2.1_20230304_part1.xlsx")
#dat2 <- read.xlsx("WFO_v2.1_20230304_part2.xlsx")
#dat3 <- read.xlsx("WFO_v2.1_20230304_part3.xlsx")
dat1 <- read.xlsx("Plants_WP_database_part1.xlsx")
dat2 <- read.xlsx("Plants_WP_database_part2.xlsx")
dat3 <- read.xlsx("Plants_WP_database_part3.xlsx")
database <- rbind(dat1, dat2, dat3)
#We are going to use the WP database but there are many differnt options
#Check here https://github.com/nameMatch/Database/tree/main

rm(dat1, dat2, dat3)

corrected.species <- nameMatch(mydata$Species..names.WFO.2,spSource=database, author = FALSE, max.distance= 1, matchFirst=TRUE)

corrected.species
#make corrections to your database if necessary
names(corrected.species)
write.csv(corrected.species, file = "corrected.species.csv")

c1<- corrected.species$Accepted_SPNAME
c2<- corrected.species$Genus_in_database
c3<- corrected.species$Family
mydata2 <- data.frame(species = c1, genus = c2, family = c3)

mytree <- phylo.maker(sp.list = mydata2, tree = GBOTB.extended.WP, nodes = nodes.info.1.WP, scenarios = "S2")
#There is available S1 and S3 and nodes.info.2.WP.csv

plot(mytree$scenario.2, cex = 0.5)





pdffn = paste0("myphylo", ".scenario2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(my.phylo.maker$scenario.2$run.1, cex = 0.5)
dev.off()
write.tree(my.phylo.maker$scenario.2, file = "mytree2.tree")



```


ML reconstruction Anthocyanins

```{r}

names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(Anthocyanins))


pdffn = paste0("Anthocyanins.pdf")
pdf(file=pdffn, width=27, height=27)
plot.phylo(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Anthocyanins[tree$tip.label],
    levels(as.factor(Anthocyanins))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=0.3)
dev.off()

fitER.Anthocyanins<-ace(Anthocyanins, tree,model="ER",type="discrete")
fitER.Anthocyanins

pdffn = paste0("ML_ER_Anthocyanins.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Anthocyanins[tree$tip.label],
    levels(as.factor(Anthocyanins))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.Anthocyanins$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.Anthocyanins<-ace(Anthocyanins,tree,model="ARD",type="discrete")
fitARD.Anthocyanins
pdffn = paste0("ML_ARD_Anthocyanins.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Anthocyanins[tree$tip.label],
    levels(as.factor(Anthocyanins))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.Anthocyanins$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping Anthocyanins
```{r}

mtree<-make.simmap(tree,Anthocyanins,model="ER", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(Anthocyanins)))

pdffn = paste0("BSM_1map_Anthocyanins.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree, cols, type="fan",ftype="i",fsize=0.6, offset=1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=0.8)
dev.off()

mtrees.Anthocyanins<-make.simmap(tree,Anthocyanins,model="ER",nsim=100)


pd.Anthocyanins<-summary(mtrees.Anthocyanins)
pd.Anthocyanins

############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Anthocyanins_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.Anthocyanins,1)[[1]],cols,fsize=0.6,ftype="i", offset = 1)
nodelabels(pie=pd.Anthocyanins$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()


obj.Anthocyanins<-densityMap(mtrees.Anthocyanins,states=levels(as.factor(Anthocyanins))[2:1],plot=FALSE)


############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Anthocyanins_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.Anthocyanins,fsize=c(0.6,1))
dev.off()
```


Phylogenetic signal of Anthocyanins
```{r}

#library(geiger)
Anthocyanins[Anthocyanins==0] <- 2
lambda.Anthocyanins <- fitDiscrete(tree, Anthocyanins, model = "ER", transform = "lambda", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Anthocyanins.bm <- fitDiscrete(tree, Anthocyanins, model = "ER", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
tree.lambda <- rescale(tree, "lambda")
tree.lambda(0)
lambda.Anthocyanins.0 <- fitDiscrete(tree.lambda(0), Anthocyanins, model = "ER", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Anthocyanins
lambda.Anthocyanins.bm
lambda.Anthocyanins.0

```



ML reconstruction Aurones

```{r}

names(mydata)
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Aurones<-Aurones[!is.na(Aurones)]
tipstoremove <- setdiff(tree$tip.label,names(Aurones))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(as.factor(Aurones)))


pdffn = paste0("Aurones.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Aurones[tree$tip.label],
    levels(as.factor(Aurones))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.Aurones<-ace(Aurones, tree,model="ER",type="discrete")
fitER.Aurones

pdffn = paste0("ML_ER_Aurones.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Aurones[tree$tip.label],
    levels(as.factor(Aurones))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.Aurones$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.Aurones<-ace(Aurones,tree,model="ARD",type="discrete")
fitARD.Aurones
pdffn = paste0("ML_ARD_Aurones.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Aurones[tree$tip.label],
    levels(as.factor(Aurones))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.Aurones$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping Aurones
```{r}

mtree<-make.simmap(tree,Aurones,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(Aurones)))

pdffn = paste0("BSM_1map_Aurones.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,type="fan",cols, fsize=0.6,ftype="i", offset = 1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.Aurones<-make.simmap(tree,Aurones,model="ARD",nsim=100)


pd.Aurones<-summary(mtrees.Aurones)
pd.Aurones


############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Aurones_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.Aurones,1)[[1]],cols,fsize=0.6,ftype="i", offset = 1)
nodelabels(pie=pd.Aurones$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()


obj.Aurones<-densityMap(mtrees.Aurones,states=levels(as.factor(Aurones))[2:1],plot=FALSE)

############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Aurones_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.Aurones,fsize=c(0.6,1))
dev.off()

```


Phylogenetic signal of Aurones
```{r}

#library(geiger)
Aurones[Aurones==0] <- 2
lambda.Aurones <- fitDiscrete(tree, Aurones, model = "ARD", transform = "lambda", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Aurones.bm <- fitDiscrete(tree, Aurones, model = "ARD", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
tree.lambda <- rescale(tree, "lambda")
tree.lambda(0)
lambda.Aurones.0 <- fitDiscrete(tree.lambda(0), Aurones, model = "ARD", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Aurones
lambda.Aurones.bm
lambda.Aurones.0

```



ML reconstruction Carotenoids

```{r}

names(mydata)
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Carotenoids<-Carotenoids[!is.na(Carotenoids)]
tipstoremove <- setdiff(tree$tip.label,names(Carotenoids))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(as.factor(Carotenoids)))


pdffn = paste0("Carotenoids.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Carotenoids[tree$tip.label],
    levels(as.factor(Carotenoids))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.Carotenoids<-ace(Carotenoids, tree,model="ER",type="discrete")
fitER.Carotenoids

pdffn = paste0("ML_ER_Carotenoids.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Carotenoids[tree$tip.label],
    levels(as.factor(Carotenoids))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.Carotenoids$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.Carotenoids<-ace(Carotenoids,tree,model="ARD",type="discrete")
fitARD.Carotenoids
pdffn = paste0("ML_ARD_Carotenoids.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Carotenoids[tree$tip.label],
    levels(as.factor(Carotenoids))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.Carotenoids$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping Carotenoids
```{r}

mtree<-make.simmap(tree,Carotenoids,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(Carotenoids)))

pdffn = paste0("BSM_1map_Carotenoids.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset = 1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.Carotenoids<-make.simmap(tree,Carotenoids,model="ARD",nsim=100)


pd.Carotenoids<-summary(mtrees.Carotenoids)
pd.Carotenoids


############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Carotenoids_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.Carotenoids,1)[[1]],cols,fsize=0.6,ftype="i", offset = 1)
nodelabels(pie=pd.Carotenoids$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE,fsize=2)
############################################
# Close PDF
############################################
dev.off()


obj.Carotenoids<-densityMap(mtrees.Carotenoids,states=levels(as.factor(Carotenoids))[2:1],plot=FALSE)


############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Carotenoids_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.Carotenoids,fsize=c(0.6,1))
dev.off()

```

Phylogenetic signal of Carotenoids
```{r}

#library(geiger)
Carotenoids[Carotenoids==0] <- 2
lambda.Carotenoids <- fitDiscrete(tree, Carotenoids, model = "ARD", transform = "lambda", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Carotenoids.bm <- fitDiscrete(tree, Carotenoids, model = "ARD", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
tree.lambda <- rescale(tree, "lambda")
lambda.Carotenoids.0 <- fitDiscrete(tree.lambda(0), Carotenoids, model = "ARD", transform = "none", niter = 1000, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Carotenoids
lambda.Carotenoids.bm
lambda.Carotenoids.0
```


ML reconstruction Chlorophylls

```{r}

names(mydata)
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Chlorophylls<-Chlorophylls[!is.na(Chlorophylls)]
tipstoremove <- setdiff(tree$tip.label,names(Chlorophylls))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(as.factor(Chlorophylls)))


pdffn = paste0("Chlorophylls.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Chlorophylls[tree$tip.label],
    levels(as.factor(Chlorophylls))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.Chlorophylls<-ace(Chlorophylls, tree,model="ER",type="discrete")
fitER.Chlorophylls

pdffn = paste0("ML_ER_Chlorophylls.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Chlorophylls[tree$tip.label],
    levels(as.factor(Chlorophylls))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.Chlorophylls$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.Chlorophylls<-ace(Chlorophylls,tree,model="ARD",type="discrete")
fitARD.Chlorophylls
pdffn = paste0("ML_ARD_Chlorophylls.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(Chlorophylls[tree$tip.label],
    levels(as.factor(Chlorophylls))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.Chlorophylls$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping Chlorophylls
```{r}

mtree<-make.simmap(tree,Chlorophylls,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(Chlorophylls)))

pdffn = paste0("BSM_1map_Chlorophylls.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset = 1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.Chlorophylls<-make.simmap(tree,Chlorophylls,model="ARD",nsim=100)


pd.Chlorophylls<-summary(mtrees.Chlorophylls)
pd.Chlorophylls



############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Chlorophylls_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plot(sample(mtrees.Chlorophylls,1)[[1]],cols,fsize=0.6,ftype="i",offset=1)
nodelabels(pie=pd.Chlorophylls$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()


obj.Chlorophylls<-densityMap(mtrees.Chlorophylls,states=levels(as.factor(Chlorophylls))[2:1],plot=FALSE)

############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_Chlorophylls_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.Chlorophylls,fsize=c(0.6,1))
dev.off()

```

Phylogenetic signal of Chlorophylls
```{r}

#library(geiger)
Chlorophylls[Chlorophylls==0] <- 2
lambda.Chlorophylls <- fitDiscrete(tree, Chlorophylls, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Chlorophylls.bm <- fitDiscrete(tree, Chlorophylls, model = "ARD", transform = "none", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
tree.lambda <- rescale(tree, "lambda")
lambda.Chlorophylls.0 <- fitDiscrete(tree.lambda(0), Chlorophylls, model = "ARD", transform = "none", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.Chlorophylls
lambda.Chlorophylls.bm
lambda.Chlorophylls.0

```


ML reconstruction number of pigments.

```{r}
library(phytools)

names(mydata)
NPigments <- mydata[,14]
names(NPigments) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

NPigments<-NPigments[!is.na(NPigments)]
tipstoremove <- setdiff(tree$tip.label,names(NPigments))
tree <- drop.tip(tree, tipstoremove)



pdffn = paste0("NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.NPigments<-ace(NPigments, tree,model="ER",type="discrete")
names(fitER.NPigments)

pdffn = paste0("ML_ER_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.NPigments<-ace(NPigments,tree,model="ARD",type="discrete")
fitARD.NPigments
pdffn = paste0("ML_ARD_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitSYM.NPigments<-ace(NPigments,tree,model="SYM",type="discrete")
fitSYM.NPigments
pdffn = paste0("ML_SYM_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitSYM.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

ARDstep <- matrix(c(0, 1, 0, 0, 2, 0, 3, 0, 0, 4, 0, 5, 0, 0, 6, 0), 4)
fitARDstep.NPigments<-ace(NPigments,tree,model=ARDstep,type="discrete")
fitARDstep.NPigments


names(mydata)
Flavonoids <- mydata[,9]
names(Flavonoids) <- mydata[,5]
Flavonoids[Flavonoids==0] <- 2
#Flavonoids[is.na(Flavonoids)] <- "3"
Flavonoids
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Anthocyanins[Anthocyanins==0] <- 2
#Anthocyanins[is.na(Anthocyanins)] <- "3"
Anthocyanins
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]
Aurones[Aurones==0] <- 2
#Aurones[is.na(Aurones)] <- "3"
Aurones
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]
Carotenoids[Carotenoids==0] <- 2
#Carotenoids[is.na(Carotenoids)] <- "3"
Carotenoids
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]
Chlorophylls[Chlorophylls==0] <- 2
#Chlorophylls[is.na(Chlorophylls)] <- "3"
Chlorophylls

#cols<-setNames(c("lightpink","#e75480","purple","#301934"),levels(as.factor(NPigments)))
cols<-setNames(c("white","lightgrey","#555555","black"),levels(as.factor(NPigments)))
cols5<-setNames(c("lightyellow","lightgrey"),levels(as.factor(Flavonoids)))
cols2<-setNames(c("blue","lightgrey"),levels(as.factor(Anthocyanins)))
cols3<-setNames(c("orange","lightgrey"),levels(as.factor(Carotenoids)))
cols4<-setNames(c("#FFCC00","lightgrey"),levels(as.factor(Aurones)))
cols6<-setNames(c("darkgreen","lightgrey"),levels(as.factor(Chlorophylls)))
node1 <- getMRCA(tree, c("Acritopappus_sp","Richterago_arenaria"))
node2 <- getMRCA(tree, c("Orchis_anthropophora","Gomesa_hydrophila"))
node3 <- getMRCA(tree, c("Clinopodium_nepeta","Stachys_ocymastrum"))
node4 <- getMRCA(tree, c("Pedicularis_sylvatica","Cistanche_phelypaea"))
node5 <- getMRCA(tree, c("Silene_adscendens","Paronychia_argentea"))
node6 <- getMRCA(tree, c("Solanum_paniculatum","Evolvulus_lithospermoides"))
node7<- getMRCA(tree, c("Trifolium_fragiferum","Hymenaea_sp"))
node8<- getMRCA(tree, c("Heliotropium_europaeum","Cynoglossum_clandestinum"))
node9<- getMRCA(tree, c("Sisymbrium_austriacum","Malcolmia_littorea"))
node10<- getMRCA(tree, c("Cistus_crispus","Malva_maroccana"))
node11<- getMRCA(tree, c("Nigella_damascena","Papaver_argemone"))
node12<- getMRCA(tree, c("Linum_trigynum","Euphorbia_segetalis"))
node13<- getMRCA(tree, c("Rosa_canina","Crataegus_monogyna"))
node14<- getMRCA(tree, c("Banisteriopsis_campestris","Byrsonima_dealbata"))
node15<- getMRCA(tree, c("Geranium_molle","Erodium_moschatum"))
node16<- getMRCA(tree, c("Cambessedesia_corymbosa","Miconia_rubiginosa"))
node17<- getMRCA(tree, c("Declieuxia_fruticosa","Asperula_hirsuta"))
node18<- getMRCA(tree, c("Cymbalaria_muralis","Linaria_spartea"))
node19<- getMRCA(tree, c("Romulea_bulbocodium","Iris_planifolia"))
node20<- getMRCA(tree, c("Allium_roseum","Acis_autumnalis"))
node21<- getMRCA(tree, c("Scilla_peruviana","Prospero_autumnale"))
node22<- getMRCA(tree, c("Xyris_asperula","Xyris_piranii"))

pdffn = paste0("ML_ARDstep_NPigments.pdf")
pdf(file=pdffn, width=30, height=30)
par(mar = c(0.1, 0.1, 0.1, 0.1))
plot(tree,type="fan",show.tip.label = T, cex = 0.1,  tip.color="white", edge.color = "grey", edge.width = 5, no.margin = F)
tiplabels(pie=to.matrix(NPigments[tree$tip.label],
    levels(as.factor(NPigments))),piecol=cols, bg=cols,cex=0.1,offset = 1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARDstep.NPigments$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=1*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Flavonoids[tree$tip.label],
    levels(as.factor(Flavonoids))),piecol=cols5, bg=cols5,cex=0.1, offset = 2.5)
add.simmap.legend(colors=cols5,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Anthocyanins[tree$tip.label],
    levels(as.factor(Anthocyanins))),piecol=cols2, bg=cols2,cex=0.1, offset = 4)
add.simmap.legend(colors=cols2,prompt=FALSE,x=0.8*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Carotenoids[tree$tip.label],
    levels(as.factor(Carotenoids))),piecol=cols3, bg=cols3,cex=0.1, offset = 5.5)
add.simmap.legend(colors=cols3,prompt=FALSE,x=0.7*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Chlorophylls[tree$tip.label],
    levels(as.factor(Chlorophylls))),piecol=cols6, bg=cols6,cex=0.1, offset = 7)
add.simmap.legend(colors=cols6,prompt=FALSE,x=0.8*par()$usr[1],
    y=0.9*par()$usr[3],fsize=2)
tiplabels(pie=to.matrix(Aurones[tree$tip.label],
    levels(as.factor(Aurones))),piecol=cols4, bg=cols4,cex=0.1, offset = 8.5)
add.simmap.legend(colors=cols4,prompt=FALSE,x=0.7*par()$usr[1],
    y=0.9*par()$usr[3],fsize=2)
arc.cladelabels(tree, "Asteraceae", node1, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Orchidaceae", node2, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Lamiaceae", node3, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Orobanchaceae", node4, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Caryophyllaceae", node5, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Solanaceae-Convolvulaceae", node6, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Fabaceae", node7, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Boraginaceae", node8, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Brassicaceae", node9, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Malvaceae-Cistaceae", node10, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Papaveraceae-Ranunculaceae", node11, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Linaceae-Euphorbiaceae", node12, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1,orientation="curved", stretch=1)
arc.cladelabels(tree, "Rosaceae", node13, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Malpighiaceae", node14, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Geraniaceae", node15, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Melastomataceae", node16, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Rubiaceae", node17, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Plantaginaceae", node18, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Iridaceae", node19, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=2,orientation="curved", stretch=1)
arc.cladelabels(tree, "Amaryllidaceae", node20, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.8,orientation="curved", stretch=1)
arc.cladelabels(tree, "Asparagaceae", node21, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
arc.cladelabels(tree, "Xyridaceae", node22, ln.offset=1.1, lab.offset=1.12,mark.node=FALSE, cex=1.5,orientation="curved", stretch=1)
dev.off()

```


Stochastic mapping Number of Pigments: This could take very long, we are not goint to do it for now.
```{r}

mtree<-make.simmap(tree,NPigments,model=ARDstep, nsim=1)
mtree
cols<-setNames(c("red","blue", "green", "yellow"),levels(as.factor(NPigments)))

pdffn = paste0("BSM_1map_NPigments.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset=1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.NPigments<-make.simmap(tree,NPigments,model=ARDstep,nsim=100)


pd.NPigments<-summary(mtrees.NPigments)
pd.NPigments



############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_NPigments_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.NPigments,1)[[1]],cols,fsize=0.6,ftype="i",offset = 1)
nodelabels(pie=pd.NPigments$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[4:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()




```

Phylogenetic signal of NPigments
```{r}

library(geiger)
NPigments[NPigments==0] <- "zero"
lambda.NPigments <- fitDiscrete(tree, NPigments, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.NPigments.bm <- fitDiscrete(tree, NPigments, model = "ARD", transform = "none", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)

tree.lambda <- rescale(tree, "lambda")
tree.lambda(0)
lambda.NPigments.0 <- fitDiscrete(tree.lambda(0), NPigments, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)

lambda.NPigments
lambda.NPigments.bm
lambda.NPigments.0

```



ML reconstruction BlueFlowers

```{r}

names(mydata)
BlueFlowers <- mydata[,15]
names(BlueFlowers) <- mydata[,5]
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

BlueFlowers<-BlueFlowers[!is.na(BlueFlowers)]
tipstoremove <- setdiff(tree$tip.label,names(BlueFlowers))
tree <- drop.tip(tree, tipstoremove)

cols<-setNames(c("red","blue"),levels(as.factor(BlueFlowers)))


pdffn = paste0("BlueFlowers.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(BlueFlowers[tree$tip.label],
    levels(as.factor(BlueFlowers))),piecol=cols,cex=0.1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitER.BlueFlowers<-ace(BlueFlowers, tree,model="ER",type="discrete")
fitER.BlueFlowers

pdffn = paste0("ML_ER_BlueFlowers.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(BlueFlowers[tree$tip.label],
    levels(as.factor(BlueFlowers))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitER.BlueFlowers$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

fitARD.BlueFlowers<-ace(BlueFlowers,tree,model="ARD",type="discrete")
fitARD.BlueFlowers
pdffn = paste0("ML_ARD_BlueFlowers.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
tiplabels(pie=to.matrix(BlueFlowers[tree$tip.label],
    levels(as.factor(BlueFlowers))),piecol=cols,cex=0.1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=fitARD.BlueFlowers$lik.anc,piecol=cols,cex=0.2)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

```


Stochastic mapping BlueFlowers
```{r}

mtree<-make.simmap(tree,BlueFlowers,model="ARD", nsim=1)
mtree
cols<-setNames(c("red","blue"),levels(as.factor(BlueFlowers)))

pdffn = paste0("BSM_1map_BlueFlowers.pdf")
pdf(file=pdffn, width=27, height=27)
plotSimmap(mtree,cols,type="fan",fsize=0.6,ftype="i", offset = 1)
add.simmap.legend(colors=cols,prompt=FALSE,x=0.9*par()$usr[1],
    y=0.8*par()$usr[3],fsize=2)
dev.off()

mtrees.BlueFlowers<-make.simmap(tree,BlueFlowers,model="ARD",nsim=100)


pd.BlueFlowers<-summary(mtrees.BlueFlowers)
pd.BlueFlowers



############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_BlueFlowers_v1.pdf")
pdf(file=pdffn, width=6, height=60)
plotSimmap(sample(mtrees.BlueFlowers,1)[[1]],cols,fsize=0.6,ftype="i", offset = 1)
nodelabels(pie=pd.BlueFlowers$ace,piecol=cols,cex=0.5)
add.simmap.legend(colors=cols[2:1],prompt=FALSE,x=0,y=-4,
    vertical=FALSE)
############################################
# Close PDF
############################################
dev.off()


obj.BlueFlowers<-densityMap(mtrees.BlueFlowers,states=levels(as.factor(BlueFlowers))[2:1],plot=FALSE)

############################################
# Open a PDF
############################################
pdffn = paste0("BSMs100_BlueFlowers_v2.pdf")
pdf(file=pdffn, width=6, height=60)
plot(obj.BlueFlowers,fsize=c(0.6,1))
dev.off()

```

Phylogenetic signal of BlueFlowers
```{r}

#library(geiger)
BlueFlowers[BlueFlowers==0] <- 2
lambda.BlueFlowers <- fitDiscrete(tree, BlueFlowers, model = "ARD", transform = "lambda", niter = 100, FAIL = 1e+200, hessian = FALSE, CI = 0.95, ncores=NULL)
lambda.BlueFlowers

```

Dependent or independen evolution

```{r}
library(phytools)

names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
Aurones<-Aurones[!is.na(Aurones)]
setdiff(names(Anthocyanins),names(Aurones))
setdiff(names(Aurones),names(Anthocyanins))
Anthocyanins <- Anthocyanins[which(names(Anthocyanins) %in% names(Aurones))]
Aurones<- Aurones[which(names(Aurones) %in% names(Anthocyanins) )]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)

x <-  Anthocyanins
x[x==0] <- "N.An"
x[x==1] <- "An"
y <- Aurones
y[y==0] <- "N.Au"
y[y==1] <- "Au"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER

fit.x.Anthocyanins.Aurones <-fit.x
pdffn = paste0("fit.x.Anthocyanins.Aurones.pdf")
pdf(file=pdffn, width=8, height=8)
plot(fit.x.Anthocyanins.Aurones,lwd.by.rate=TRUE,
    main=c("a) Independent model",
    "b) Dependent (Anthocyanins | Aurones) model"))
dev.off()

names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
Carotenoids<-Carotenoids[!is.na(Carotenoids)]
setdiff(names(Anthocyanins),names(Carotenoids))
setdiff(names(Carotenoids),names(Anthocyanins))
Anthocyanins <- Anthocyanins[which(names(Anthocyanins) %in% names(Carotenoids))]
Carotenoids<- Carotenoids[which(names(Carotenoids) %in% names(Anthocyanins) )]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)

x <-  Anthocyanins
x[x==0] <- "N.An"
x[x==1] <- "An"
y <- Carotenoids
y[y==0] <- "N.Ca"
y[y==1] <- "Ca"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER

fit.x.Anthocyanins.Carotenoids <-fit.x
pdffn = paste0("fit.x.Anthocyanins.Carotenoids.pdf")
pdf(file=pdffn, width=8, height=8)
plot(fit.x.Anthocyanins.Carotenoids,lwd.by.rate=TRUE,
    main=c("a) Independent model",
    "b) Dependent (Anthocyanins | Carotenoids) model"))
dev.off()


names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
Chlorophylls<-Chlorophylls[!is.na(Chlorophylls)]
setdiff(names(Anthocyanins),names(Chlorophylls))
setdiff(names(Chlorophylls),names(Anthocyanins))
Anthocyanins <- Anthocyanins[which(names(Anthocyanins) %in% names(Chlorophylls))]
Chlorophylls<- Chlorophylls[which(names(Chlorophylls) %in% names(Anthocyanins) )]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)

x <-  Anthocyanins
x[x==0] <- "N.An"
x[x==1] <- "An"
y <- Chlorophylls
y[y==0] <- "N.Ch"
y[y==1] <- "Ch"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER


names(mydata)
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Aurones<-Aurones[!is.na(Aurones)]
Carotenoids<-Carotenoids[!is.na(Carotenoids)]
setdiff(names(Aurones),names(Carotenoids))
setdiff(names(Carotenoids),names(Aurones))
Aurones <- Aurones[which(names(Aurones) %in% names(Carotenoids))]
Carotenoids<- Carotenoids[which(names(Carotenoids) %in% names(Aurones) )]
tipstoremove <- setdiff(tree$tip.label,names(Aurones))
tree <- drop.tip(tree, tipstoremove)

x <-  Aurones
x[x==0] <- "N.Au"
x[x==1] <- "Au"
y <- Carotenoids
y[y==0] <- "N.Ca"
y[y==1] <- "Ca"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER
  

names(mydata)
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Aurones<-Aurones[!is.na(Aurones)]
Chlorophylls<-Chlorophylls[!is.na(Chlorophylls)]
setdiff(names(Aurones),names(Chlorophylls))
setdiff(names(Chlorophylls),names(Aurones))
Aurones <- Aurones[which(names(Aurones) %in% names(Chlorophylls))]
Chlorophylls<- Chlorophylls[which(names(Chlorophylls) %in% names(Aurones) )]
tipstoremove <- setdiff(tree$tip.label,names(Aurones))
tree <- drop.tip(tree, tipstoremove)

x <-  Aurones
x[x==0] <- "N.Au"
x[x==1] <- "Au"
y <- Chlorophylls
y[y==0] <- "N.Ch"
y[y==1] <- "Ch"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER

fit.xy.Aurones.Chlorophylls <-fit.xy
pdffn = paste0("fit.xy.Aurones.Chlorophylls.pdf")
pdf(file=pdffn, width=8, height=8)
plot(fit.xy.Aurones.Chlorophylls,lwd.by.rate=TRUE,
    main=c("a) Independent model",
    "b) Dependent (Aurones | Chlorophylls) model"))
dev.off()

#Dependent (x & y) model rate matrix:
#                Au|Ch      Au|N.Ch      N.Au|Ch    N.Au|N.Ch
#Au|Ch     -0.05872631  0.023052923  0.035673388  0.000000000
#Au|N.Ch    0.00000000 -0.061260843  0.000000000  0.061260843
#N.Au|Ch    0.00000000  0.000000000 -0.023353560  0.023353560
#N.Au|N.Ch  0.00000000  0.002789035  0.005895684 -0.008684719
#Model fit:
#            log-likelihood      AIC
#independent      -274.3709 556.7418
#dependent        -269.4757 554.9514
fit.xy.c<-fitPagel2(tree,x,y, dep.var = "xyc")
fit.xy.c
pdffn = paste0("fit.xy.c.Aurones.Chlorophylls.pdf")
pdf(file=pdffn, width=8, height=8)
plot(fit.xy.c,lwd.by.rate=TRUE,
    main=c("a) Independent model",
    "b) Dependent (Aurones | Chlorophylls) model (constrained)"))
dev.off()


names(mydata)
Carotenoids <- mydata[,12]
names(Carotenoids) <- mydata[,5]
Chlorophylls <- mydata[,13]
names(Chlorophylls) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Carotenoids<-Carotenoids[!is.na(Carotenoids)]
Chlorophylls<-Chlorophylls[!is.na(Chlorophylls)]
setdiff(names(Carotenoids),names(Chlorophylls))
setdiff(names(Chlorophylls),names(Carotenoids))
Carotenoids <- Carotenoids[which(names(Carotenoids) %in% names(Chlorophylls))]
Chlorophylls<- Chlorophylls[which(names(Chlorophylls) %in% names(Carotenoids) )]
tipstoremove <- setdiff(tree$tip.label,names(Carotenoids))
tree <- drop.tip(tree, tipstoremove)

x <-  Carotenoids
x[x==0] <- "N.Ca"
x[x==1] <- "Ca"
y <- Chlorophylls
y[y==0] <- "N.Ch"
y[y==1] <- "Ch"
fit.xy<-fitPagel(tree,x,y)
fit.x<-fitPagel(tree,x,y,dep.var="x")
fit.y<-fitPagel(tree,x,y,dep.var="y")
fit.xy.ER<-fitPagel(tree,x,y, model = "ER")
fit.x.ER<-fitPagel(tree,x,y,dep.var="x",model = "ER")
fit.y.ER<-fitPagel(tree,x,y,dep.var="y",model = "ER")

fit.xy
fit.x
fit.y
fit.xy.ER
fit.x.ER
fit.y.ER

```


Analyses with corHMM
```{r}

library(corHMM)

names(mydata)
Anthocyanins <- cbind (as.character(mydata[,5][!is.na(mydata[,10])]),mydata[,10][!is.na(mydata[,10])])
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Anthocyanins[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Anthocyanins<-corHMM(tree,Anthocyanins,rate.cat=2,node.states="marginal")
pp.Anthocyanins
pp.Anthocyanins.1<-corHMM(tree,Anthocyanins,rate.cat=1,node.states="marginal")
pp.Anthocyanins.1
pp.Anthocyanins.2<-corHMM(tree,Anthocyanins,rate.cat=2, model = "ER", node.states="marginal")
pp.Anthocyanins.2
pp.Anthocyanins.3<-corHMM(tree,Anthocyanins,rate.cat=1, model = "ER", node.states="marginal")
pp.Anthocyanins.3

simmap.Anthocyanins <- makeSimmap(tree=tree, data=Anthocyanins, model=pp.Anthocyanins.2$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Anthocyanins)

pdffn = paste0("Anthocyanins2rates.ER.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Anthocyanins.2$states,cex=0.5, pie.cex=0.5,title="Anthocyanins 2 rates ER")
dev.off()

pdffn = paste0("Anthocyanins2rates.ER.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Anthocyanins.2$states,cex=0.5, pie.cex=0.5,title="Anthocyanins 2 rates ER")
dev.off()


cols<-setNames(c("white", "black", "red", "yellow"),levels(c("(0,R1)", "(1,R1)", "(0,R2)", "(1,R2)")))
pdffn = paste0("Anthocyanins2ratesfanER.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Anthocyanins.2$states,piecol=cols,cex=0.2)
dev.off()


names(mydata)
Aurones <- cbind (as.character(mydata[,5][!is.na(mydata[,11])]),mydata[,11][!is.na(mydata[,11])])
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Aurones[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Aurones<-corHMM(tree,Aurones,rate.cat=2,node.states="marginal")
pp.Aurones
pp.Aurones.1<-corHMM(tree,Aurones,rate.cat=1,node.states="marginal")
pp.Aurones.1
pp.Aurones.2<-corHMM(tree,Aurones,model = "ER", rate.cat=2,node.states="marginal")
pp.Aurones.2
pp.Aurones.3<-corHMM(tree,Aurones,model = "ER", rate.cat=1,node.states="marginal")
pp.Aurones.3

simmap.Aurones <- makeSimmap(tree=tree, data=Aurones, model=pp.Aurones$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Aurones)

pdffn = paste0("Aurones2rates.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Aurones$states,cex=0.5, pie.cex=0.5,title="Aurones 2 rates")
dev.off()


cols<-setNames(c("white", "black", "red", "yellow"),levels(c("(0,R1)", "(1,R1)", "(0,R2)", "(1,R2)")))
pdffn = paste0("Aurones2ratesfan.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Aurones$states,piecol=cols,cex=0.2)
dev.off()


names(mydata)
Carotenoids <- cbind (as.character(mydata[,5][!is.na(mydata[,12])]),mydata[,12][!is.na(mydata[,12])])
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Carotenoids[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Carotenoids<-corHMM(tree,Carotenoids,rate.cat=2,node.states="marginal")
pp.Carotenoids
pp.Carotenoids.1<-corHMM(tree,Carotenoids,rate.cat=1,node.states="marginal")
pp.Carotenoids.1
pp.Carotenoids.2<-corHMM(tree,Carotenoids,model = "ER", rate.cat=2,node.states="marginal")
pp.Carotenoids.2
pp.Carotenoids.3<-corHMM(tree,Carotenoids,model = "ER", rate.cat=1,node.states="marginal")
pp.Carotenoids.3

simmap.Carotenoids <- makeSimmap(tree=tree, data=Carotenoids, model=pp.Carotenoids$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Carotenoids)

pdffn = paste0("Carotenoids2rates.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Carotenoids$states,cex=0.5, pie.cex=0.5,title="Carotenoids 2 rates")
dev.off()


cols <- c("white", "black", "red", "yellow")
pdffn = paste0("Carotenoids2ratesfan.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Carotenoids$states,piecol=cols,cex=0.2)
dev.off()


names(mydata)
Chlorophylls <- cbind (as.character(mydata[,5][!is.na(mydata[,13])]),mydata[,13][!is.na(mydata[,13])])
tree <- multi2di(my.phylo.maker$scenario.2$run.1)
library(phytools)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6
tipstoremove <- setdiff(tree$tip.label,Chlorophylls[,1])
tree <- drop.tip(tree, tipstoremove)

pp.Chlorophylls<-corHMM(tree,Chlorophylls,rate.cat=2,node.states="marginal")
pp.Chlorophylls
pp.Chlorophylls.1<-corHMM(tree,Chlorophylls,rate.cat=1,node.states="marginal")
pp.Chlorophylls.1
pp.Chlorophylls.2<-corHMM(tree,Chlorophylls,model = "ER", rate.cat=2,node.states="marginal")
pp.Chlorophylls.2
pp.Chlorophylls.3<-corHMM(tree,Chlorophylls,model = "ER",rate.cat=1,node.states="marginal")
pp.Chlorophylls.3

simmap.Chlorophylls <- makeSimmap(tree=tree, data=Chlorophylls, model=pp.Chlorophylls$solution, rate.cat=2, nSim=100, nCores=1)
summary(simmap.Chlorophylls)

pdffn = paste0("Chlorophylls2rates.pdf")
pdf(file=pdffn, width=6, height=60)
plotRECON(tree,pp.Chlorophylls$states,cex=0.5, pie.cex=0.5,title="Chlorophylls 2 rates")
dev.off()


cols <- c("white", "black", "red", "yellow")
pdffn = paste0("Chlorophylls2ratesfan.pdf")
pdf(file=pdffn, width=27, height=27)
plot(tree,type="fan",cex=0.6,font=3,lwd=1)
nodelabels(node=1:tree$Nnode+Ntip(tree),
    pie=pp.Chlorophylls$states,piecol=cols,cex=0.2)
dev.off()
















names(mydata)
Anthocyanins <- mydata[,10]
names(Anthocyanins) <- mydata[,5]
Aurones <- mydata[,11]
names(Aurones) <- mydata[,5]

tree <- multi2di(my.phylo.maker$scenario.1)
tree$edge.length[tree$edge.length==0]<-max(nodeHeights(tree))*1e-6

Anthocyanins<-Anthocyanins[!is.na(Anthocyanins)]
Aurones<-Aurones[!is.na(Aurones)]
setdiff(names(Anthocyanins),names(Aurones))
setdiff(names(Aurones),names(Anthocyanins))
Anthocyanins <- Anthocyanins[which(names(Anthocyanins) %in% names(Aurones))]
Aurones<- Aurones[which(names(Aurones) %in% names(Anthocyanins) )]
tipstoremove <- setdiff(tree$tip.label,names(Anthocyanins))
tree <- drop.tip(tree, tipstoremove)
Anthocyanins.Aurones <- cbind(names(Anthocyanins), Anthocyanins, Aurones)


#pp.Anthocyanins.Aurones.ER.null<-corDISC(tree,Anthocyanins.Aurones,ntraits=2,model="ER", node.states="marginal")
#pp.Anthocyanins.Aurones.ER.null
#pp.Anthocyanins.Aurones.ARD.null<-corDISC(tree,Anthocyanins.Aurones,ntraits=2,model="ARD", node.states="marginal")
#pp.Anthocyanins.Aurones.ARD.null
#pp.Anthocyanins.Aurones.paint<-corPAINT(tree,Anthocyanins.Aurones,ntraits=2,model=c("ER","ARD"), node.states="marginal")
#pp.Anthocyanins.Aurones.paint
#We need here a column to define the selective regimes!!!!! Ask to Edur

```

